### 2019-11-14 docs/report_latex/template.tex
Initial Report

\documentclass[a4paper]{article}

%use the english line for english reports
\usepackage[english]{babel}
%\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{url}

\begin{document}

\setlength{\textwidth}{16cm}
\setlength{\textheight}{22cm}

\title{\Huge\textbf{Mbrane}\linebreak\linebreak\linebreak
\Large\textbf{Final Report}\linebreak\linebreak
\linebreak\linebreak
\includegraphics[scale=0.1]{feup-logo.png}\linebreak\linebreak
\linebreak\linebreak
\Large{Logic Programing}\linebreak
}

\author{\textbf{Group Mbrane 4:}\\ Leonardo Fernandes Moura - 201706907@fe.up.pt \\ João Pedro Campos - up201704982@fe.up.pt \\\linebreak\linebreak \\
 \\ Faculdade de Engenharia da Universidade do Porto \\ Rua Roberto Frias, s\/n, 4200-465 Porto, Portugal \linebreak\linebreak\linebreak
\linebreak\linebreak\vspace{1cm}}
\date{November 13, 2019}
\maketitle
\thispagestyle{empty}

%************************************************************************************************
%************************************************************************************************

\newpage

% TODO
\section*{Summary}
Resumo do trabalho (aprox. 250 palavras) descrevendo sucintamente o problema abordado, objetivos, metodologia usada na sua resolução, principais resultados e conclusões).

\paragraph{} 
The goal of this project was to program a board game using the prolog language. In our case the game in question is Mbrane, a 
game created by DukeZhou based on Sudoku and strategy games like chess. Section 2 clarifies all the aspects of this game.

\paragraph{}
In terms of programing, the goal of the project was to efficiently implement all the game logic using Prolog.  This means we have to
represent the core mechanics of the game using Prolog. The first step is to find a way to represent the game board that's both 
efficient and relatively simple to program and operate. Then our goal is to make the game playable, continuously updating the state of
the board as both players make their moves. In order to termiate the game and find the winner, we need to detect when the board is in a completed 
state, then we calculate the winner and present it. After the game is playable, the final step is to make it possible to play against the computer 
programing a bot that would be able to play in two difficulty settings. The first one (the easy mode) simply makes random plays, the second 
one calculates the best play it can make at the moment (greedy approach). This means we end up with three different game modes: player versus player,
player versus bot and bot versus bot.

\paragraph{}
Besides all the game logic, the player needs to interact with the game, so we need to develop a simple text base UI, using
Prolog predicates that are able to interact with the terminal input/output stream. This allows us to read inputs from the
player (or both players) so that we can use them make moves.

\paragraph{}
The prolog distribution used was SicStus Prolog using a Student License.

\newpage

\tableofcontents

%************************************************************************************************
%************************************************************************************************

%*************************************************************************************************
%************************************************************************************************

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO complete
\section{Introduction}
\paragraph{}
This project was developed during the Logic Programing Course in the context of the third the Integrated Masters in Informatics 
and Computing Engineering. The goal is to implement in Prolog a board game, in this case \textit{Mbrane}.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\section{Game Presentation}

\subsection{Origin}

\paragraph{}
Mbrane is a fairly recent game. It was created in 2013 by someone who goes by the name of DukeZhou. 
When he was a kid, DukeZhou really liked to play strategy board games, but he didn’t like games where luck was a 
relevant factor, he liked games where the player with superior strategy or the one “who played better” was definitely the winner. 
Games like chess or checkers were all he was into. n 2005 he discovered Sudoku, and even though puzzles were not his favorite type 
of game, he was amazed by the game. The sheer amount of combinations for a 9x9 board is around $6.7*10^21$. That factor combined with 
the all restraints the puzzle imposes made it feel somewhat magical.

\paragraph{}
In May 2013 while he was playing Fallout 3 the rules of Mbrane dropped into his head all at once. He immediately called a friend whom
he used to play chess with and they spent hours playing and discovering the game, getting more and more fascinated with it as time went by.

\paragraph{}
The full story, taken from the journals of DukeZhou can be read in the following address: 
http://mbranegame.com/origin-of-mbrane \cite{Origin}.

\subsection{Rules}
The following rules are the official rules for Mbrane, in their integral redaction.
Mbrane is divided in two distinct phases: the placement phase and the resolution phase

\subsubsection{Placement phase}
\begin{itemize}
    \item Players take turns placing numbers in an empty Sudoku. These are bids for territories. 
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_1.png}
\end{center}

\pagebreak
\begin{itemize}
    \item Players receive points equal to the number in the region where the number is placed. These points 
    are known as \textbf{Power}.
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_2.png}
\end{center}

\begin{itemize}
    \item If a number borders other regions, horizontally, vertically or diagonally, the player receives 
    1/2 points in those border regions.  These points are known as \textbf{Influence}.
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_3.png}
\end{center}

\begin{itemize}
    \item Placement conforms to the rules of Sudoku, so a number may only be placed once in a region, row or 
    column. (Broken Sudoku will occur.)
    \item When all numbers that can be placed have been placed, the gameboard is resolved. \textbf{Resolution} 
    determines the outcome.
\end{itemize}

\pagebreak
\subsubsection{Resolution Phase}

\begin{itemize}
    \item Regions are resolved in order of the greatest disparity. These are the regions with greatest point 
    difference between players.
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_4.png}
\end{center}

\begin{itemize}
    \item When a region is resolved, it is awarded to the player with the most points in the region, known as the dominant player.
    \item All opposing numbers in that region defect, flipping to the dominant player. This player is now said to have control.
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_5.png}
\end{center}

\begin{itemize}
    \item If these numbers border other regions, they switch their \textbf{Influence} points. (This can shift the balance of power, 
    affecting the outcome of the game!)
\end{itemize}
\begin{center}
    \includegraphics[scale=0.5]{img/tutorial_6.png}
\end{center}

\begin{itemize}
    \item When all regions that can be resolved, have been resolved, the player controlling the most regions wins.
    \item Strength of victory is measured by the ratio of controlled regions between players, such as 5/4, 4/5, 4/4, 9/0, 0/9,\ldots
\end{itemize}

\paragraph{}
The official rules can be consulted in the address: http://mbranegame.com/rules-of-m \cite{Rules}.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\section{Game Logic}

Descrever o projeto e implementação da lógica do jogo em Prolog, incluindo a forma de representação do estado do tabuleiro e sua visualização, execução de movimentos, verificação do cumprimento das regras do jogo, determinação do final do jogo e cálculo das jogadas a realizar pelo computador utilizando diversos níveis de jogo. Sugere-se a estruturação desta secção da seguinte forma:

% TODO complete
\subsection{Game state representation} 
Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
boards represented in the game’s data structures. There’s a board predicate that represents the game board itself, a
list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
also a \textbf{board\_blocks} predicate. This predicate is also a list of 9 lists, each one representing a 3 by 3 block of the 
board, this is used to facilitate calculations involving power in each block and influence in adjacent blocks caused 
by the placement of a number in the edge of a block. Finally we have a \textbf{board\_influence} list that stores the values of 
power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
updated accordingly.

% TODO complete
\subsection{Board viewing} 
Descrever a interface com o utilizador, descrevendo a visualização do estado do jogo (pode ser idêntico ao descrito no relatório intercalar) e robustez da interface/validações de entrada.

% TODO complete
\subsection{List valid plays} 
Obtenção de uma lista de jogadas possíveis. O predicado deve chamar-se \textit{valid\_moves(+Board, +Player, -ListOfMoves)}.

% TODO complete
\subsection{Play execution} 
Validação e execução de uma jogada num tabuleiro, obtendo o novo estado do jogo. O predicado deve chamar-se \textit{move(+Move, +Board, -NewBoard)}.

\paragraph{}
The number placing rules are the ones of Sudoku, so the player can only place a number if that same number is not present
in either the column, row or 3x3 section of the square the player wants to place it. If these conditions are met, 
the number is able to be placed.

% TODO complete
\subsection{Game finalization} 
Verificação do fim do jogo, com identificação do vencedor. O predicado deve chamar-se \textit{game\_over(+Board, -Winner)}.

\paragraph{}
The game is in the final state if no more numbers can be placed on the board. When this happens the game enters the 
\textbf{Resolution Phase} and proceds to make the calculartions mentioned in \textbf{Section 2}. Then the winner (if it exists) is
announced.

% TODO complete
\subsection{Board evaluation}
Avaliação do estado do jogo, que permitirá comparar a aplicação das diversas jogadas disponíveis. O predicado deve chamar-se \textit{value(+Board, +Player, -Value)}.

% TODO complete
\subsection{Plays of the computer} 
Escolha da jogada a efetuar pelo computador, dependendo do nível de dificuldade. O predicado deve chamar-se \textit{choose\_move(+Board, +Level, -Move)}.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
% TODO complete
\section{Conclusions}
Que conclui deste projecto? Como poderia melhorar o trabalho desenvolvido?

\clearpage
%\addcontentsline{toc}{section}{Bibliografia}
\renewcommand\refname{Apendix}
\bibliographystyle{apalike}
\bibliography{myrefs}

\newpage
\appendix
% \section{Nome do Anexo}
% Outros elementos úteis que não sejam essenciais ao relatório.

\end{document}

### 2019-11-14 src/board.pl
Kill me pls

@@ -1,6 +1,6 @@
-:-dynamic(board/1).
-:-dynamic(board_blocks/1).
-:-dynamic(board_influence/1).
+% :- dynamic(board/1).
+% :- dynamic(board_blocks/1).
+% :- dynamic(board_influence/1).
 
 % starting board list of lines
 board([
@@ -31,74 +31,73 @@ board_influence([0, 0, 0, 0, 0, 0, 0, 0, 0]).
 
 % destroy_board
 % BL, BB, BI - return boards
-destroy_board(BL, BB, BI):-board(BL), retract(board(BL)), board_blocks(BB), retract(board_blocks(BB)), board_influence(BI), retract(board_influence(BI)).
+destroy_board(BL, BB, BI):- board(BL), retract(board(BL)), board_blocks(BB), retract(board_blocks(BB)), board_influence(BI), retract(board_influence(BI)).
 
 % save_board
 % BL, BB, BI - boards to assert
-save_board(BL, BB, BI):-assertz(board(BL)), assertz(board_blocks(BB)), assertz(board_influence(BI)).
+save_board(BL, BB, BI):- assertz(board(BL)), assertz(board_blocks(BB)), assertz(board_influence(BI)).
 
 % make_move
 % X, Y 	- coordinates
 % V		- value
-make_move(X, Y, V, BL, BB, BI, RL, RB, RI):-check_move(X, Y, V, BL, BB), !, place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
+make_move(X, Y, V, BL, BB, BI, RL, RB, RI):- check_move(X, Y, V, BL, BB), !, place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
 
 % check_move
 % X, Y 	- coordinates
 % V 	- value
-check_move(X, Y, V, BL, BB):-check_x(X), check_y(Y), check_v(V), check_cell(X, Y, BL), check_restrictions(X, Y, V, BL, BB).
-check_move(_, _, _, _):-write('error move'), nl, fail.
+check_move(X, Y, V, BL, BB):- check_x(X), check_y(Y), check_v(V), check_cell(X, Y, BL), check_restrictions(X, Y, V, BL, BB).
+check_move(_, _, _, _):- write('error move'), nl, fail.
 
 % check_move auxiliar
[…]

### 2019-11-14 src/display.pl

@@ -1,20 +1,20 @@
-display_board(B):-display_board(B, 9).
-display_board(_, 0):-write('+---+---+---+---+---+---+---+---+---+'), nl.
-display_board([L|T], I):-
+display_board(B):- display_board(B, 9).
+display_board(_, 0):- write('+---+---+---+---+---+---+---+---+---+'), nl.
+display_board([L|T], I):- 
 	I > 0, !,
 	write('+---+---+---+---+---+---+---+---+---+'), nl,
 	draw_line(L), nl,
 	NI is I - 1,
 	display_board(T, NI).
 
-draw_line(L):-draw_line(L, 9).
-draw_line(_, 0):-write('|').
-draw_line([H|T], J):-
+draw_line(L):- draw_line(L, 9).
+draw_line(_, 0):- write('|').
+draw_line([H|T], J):- 
 	J > 0, !,
 	write('| '), write(H), write(' '),
 	NJ is J - 1,
 	draw_line(T, NJ).
 
-display_game(B, P):-
+display_game(B, P):- 
     game_ui(P),
     display_board(B).

### 2019-11-14 src/mbrane.pl

@@ -1,62 +1,92 @@
-:-use_module(library(lists)).
+:- use_module(library(lists)).
 
-:-include('util.pl').
-:-include('menu.pl').
-:-include('board.pl').
-:-include('display.pl').
+:- include('util.pl').
+:- include('menu.pl').
+:- include('board.pl').
+:- include('display.pl').
 
-mbrane:-main_menu(OP), repeat, mbrane(OP).
-mbrane('0'):-game, fail.
-mbrane('1'):-instructions_menu, fail.
-mbrane('2'):-about_menu, fail.
-mbrane(_):-!.
+mbrane:- main_menu(OP), repeat, mbrane(OP).
+mbrane('0'):- game, fail.
+mbrane('1'):- instructions_menu, fail.
+mbrane('2'):- about_menu, fail.
+mbrane(_):- !.
 
-game:-player_select(OP), repeat, game(OP).
-game('0'):-game_2players, fail.
-game('1'):-game_player_bot, fail.
-game('2'):-game_2bots, fail.
-game(_):-!.
+game:- player_select(OP), repeat, game(OP).
+game('0'):- game_2players, fail.
+game('1'):- game_player_bot, fail.
+game('2'):- game_2bots, fail.
+game(_):- !.
 
-display_game(B, P1, P2):-game_ui(P1, P2), display_board(B).
+display_game(B, P1, P2):- game_ui(P1, P2), display_board(B).
 
-game_2players:-
+game_2players:- 
 	get_player(P1),
 	get_player(P2),
-	repeat,
-		% game main loop
-		game_loop_2players(P1, P2),
+	game_loop_2players(P1,P2,0);
 	wait_enter.
 
-game_player_bot:-
+game_player_bot:- 
 	board(BB),
 	get_player(Player),
 	display_game(BB, Player, "Bot"),
 	wait_enter.
 
-game_2bots:-
+game_2bots:- 
 	board(BB),
 	display_game(BB, "Bot1", "Bot2"),
 	wait_enter.
 
-game_loop_2players(P1, P2):-
+% game_loop_2players(P1, P2):- 
+% 	% Player 1 plays
+% 	destroy_board(BL1, BB1, BI1),
+% 	display_game(BL1, P1, P2),
+% 	repeat,
+% 		player_turn(BL1, BB1, BI1, 1),
+% 	% Player 2 plays
[…]

### 2019-11-14 src/menu.pl

@@ -1,4 +1,4 @@
-main_menu(OP):-
+main_menu(OP):- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|                  Mbrane                  |'), nl,
@@ -11,7 +11,7 @@ main_menu(OP):-
     write('+------------------------------------------+'), nl,
     get_option('Option: ', OP).
 
-player_select(OP):-
+player_select(OP):- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|             Select Game Mode             |'), nl,
@@ -24,7 +24,7 @@ player_select(OP):-
     write('+------------------------------------------+'), nl,
     get_option('Option: ', OP).
 
-instructions_menu:-
+instructions_menu:- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|               Instructions               |'), nl,
@@ -38,7 +38,7 @@ instructions_menu:-
     write('+------------------------------------------+'), nl,
     wait_enter.
 
-about_menu:-
+about_menu:- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|                   About                  |'), nl,
@@ -54,7 +54,7 @@ about_menu:-
     write('+------------------------------------------+'), nl,
     wait_enter.
 
-game_ui(Player1, Player2):-
+game_ui(Player1, Player2):- 
     nl, nl, nl, nl,
     format('~s~n', [Player1]),
     format('                 ~p~n', 'VS'),

### 2019-11-14 src/util.pl

@@ -1,36 +1,50 @@
 % get_option
 % Option    - return option
-get_option(M, O):-
+get_option(M, O):- 
     write(M),
     get_char(O),
     get_char(_).
 
-get_int(M, I):-
+get_int(M, I):- 
     write(M),
     get_code(C),
-    get_char(_),
+    C > 47,
+    C < 58,
+    get_code(10),
     I is C - 48.
 
-wait_enter:-get_char(_).
+get_int(M,I) :- 
+    write('Invalid number\n'),
+    get_int(M,I).
+
+wait_enter:- get_char(_).
+
+abs(N,Abs) :- 
+    N  >=  0,
+    Abs = N.
+
+abs(N,Abs) :- 
+    N < 0,
+    Abs is -N.
 
 get_string_(10, Acc, Acc).
 
-get_string_(Ch, Acc, String):-
+get_string_(Ch, Acc, String):- 
     get_code(NCh),
     get_string_(NCh, [Ch|Acc], String).
 
-get_string(String):-
+get_string(String):- 
     get_code(Ch),
     get_string_(Ch, [], InvString),
     reverse(InvString, String).
 
-get_player(Player):-
+get_player(Player):- 
 	write('Player name'), nl,
 	write('     ?- '),
 	get_string(Player).
 
 % wait_enter
-wait_enter:-get_char(_).
+wait_enter:- get_char(_).
 
 % replace
 % List      - list to replace
@@ -38,7 +52,7 @@ wait_enter:-get_char(_).
 % Value     - value to replace
 % NewList   - return list
 replace([_|T], 0, V, [V|T]).
-replace([H|T], I, V, [H|R]):-I > 0, NI is I - 1, replace(T, NI, V, R), !.
+replace([H|T], I, V, [H|R]):- I > 0, NI is I - 1, replace(T, NI, V, R), !.
 
 % replace_matrix
 % Matrix    - matrix to replace
@@ -46,20 +60,23 @@ replace([H|T], I, V, [H|R]):-I > 0, NI is I - 1, replace(T, NI, V, R), !.
 % Y         - y coordinate of cell
 % Value     - value to replace
 % NewMatrix - return matrix
-replace_matrix([C|L], X, 0, V, [F|L]):-replace(C, X, V, F).
-replace_matrix([F|L], X, Y, V, [F|R]):-Y > 0, NY is Y - 1, replace_matrix(L, X, NY, V, R), !.
[…]

### 2019-11-16 src/board.pl
Can place pieces anywhere in the board. Need to had restrictions.

@@ -1,7 +1,3 @@
-% :- dynamic(board/1).
-% :- dynamic(board_blocks/1).
-% :- dynamic(board_influence/1).
-
 % starting board list of lines
 board([
 	[' ', ' ', ' ', ' ', ' ', ' ', ' ', ' ', ' '],
@@ -29,75 +25,98 @@ board_blocks([
 % starting board list of influences
 board_influence([0, 0, 0, 0, 0, 0, 0, 0, 0]).
 
-% destroy_board
-% BL, BB, BI - return boards
-destroy_board(BL, BB, BI):- board(BL), retract(board(BL)), board_blocks(BB), retract(board_blocks(BB)), board_influence(BI), retract(board_influence(BI)).
-
-% save_board
-% BL, BB, BI - boards to assert
-save_board(BL, BB, BI):- assertz(board(BL)), assertz(board_blocks(BB)), assertz(board_influence(BI)).
+% get starting boards
+start_board([BL,BB,BI]) :- board(BL), board_blocks(BB), board_influence(BI).
 
 % make_move
-% X, Y 	- coordinates
-% V		- value
-make_move(X, Y, V, BL, BB, BI, RL, RB, RI):- check_move(X, Y, V, BL, BB), !, place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
+make_move([X, Y], V, [BL, BB, BI], [RL, RB, RI]) :- check_move(X, Y, V, BL, BB), place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
+make_move(_, _, _, _) :- msg('error move'), fail.
 
 % check_move
-% X, Y 	- coordinates
-% V 	- value
-check_move(X, Y, V, BL, BB):- check_x(X), check_y(Y), check_v(V), check_cell(X, Y, BL), check_restrictions(X, Y, V, BL, BB).
-check_move(_, _, _, _):- write('error move'), nl, fail.
+check_move(X, Y, V, BL, BB) :- 
+	check_x(X), check_y(Y), check_v(V), 
+	check_cell(X, Y, BL), check_restrictions(X, Y, V, BL, BB).
 
 % check_move auxiliar
-check_x(X):- X  >=  0, X =< 8.
-check_y(Y):- Y  >=  0, Y =< 8.
-check_v(V):- abs(V,Abs),Abs  >=  0, Abs =< 8.
[…]

### 2019-11-16 src/display.pl

@@ -1,20 +1,24 @@
-display_board(B):- display_board(B, 9).
-display_board(_, 0):- write('+---+---+---+---+---+---+---+---+---+'), nl.
-display_board([L|T], I):- 
-	I > 0, !,
-	write('+---+---+---+---+---+---+---+---+---+'), nl,
+display_board(B) :- 
+	write('     0   1   2   3   4   5   6   7   8  '), nl,
+	display_board(B, 8).
+display_board([L|T], I) :- 
+	I >= 0,
+	write('   +---+---+---+---+---+---+---+---+---+'), nl,
+	N is 8 - I, write(' '), write(N), write(' '),
 	draw_line(L), nl,
 	NI is I - 1,
 	display_board(T, NI).
+display_board(_, -1) :- write('   +---+---+---+---+---+---+---+---+---+'), nl.
 
-draw_line(L):- draw_line(L, 9).
-draw_line(_, 0):- write('|').
-draw_line([H|T], J):- 
-	J > 0, !,
-	write('| '), write(H), write(' '),
+draw_line(L) :- draw_line(L, 9).
+draw_line(_, 0) :- write('|').
+draw_line([H|T], J) :- 
+	J > 0, (H = ' ', V = ' '; abs(H,V)),
+	write('| '), write(V), write(' '),
 	NJ is J - 1,
 	draw_line(T, NJ).
 
-display_game(B, P):- 
-    game_ui(P),
-    display_board(B).
+
+display_power(P) :- write(' 0 1 2 3 4 5 6 7 8 '),nl,write('|'),display_power_(P).
+display_power_([]) :- nl.
+display_power_([P|T]) :- write(P), write('|'), display_power_(T).

### 2019-11-16 src/mbrane.pl

@@ -1,92 +1,73 @@
-:- use_module(library(lists)).
+ :- use_module(library(lists)).
 
-:- include('util.pl').
-:- include('menu.pl').
-:- include('board.pl').
-:- include('display.pl').
+ :- include('util.pl').
+ :- include('menu.pl').
+ :- include('board.pl').
+ :- include('display.pl').
 
-mbrane:- main_menu(OP), repeat, mbrane(OP).
-mbrane('0'):- game, fail.
-mbrane('1'):- instructions_menu, fail.
-mbrane('2'):- about_menu, fail.
-mbrane(_):- !.
+mbrane :- main_menu(OP), repeat, mbrane(OP).
+mbrane('0') :- game, fail.
+mbrane('1') :- instructions_menu, fail.
+mbrane('2') :- about_menu, fail.
+mbrane(_) :- true.
 
-game:- player_select(OP), repeat, game(OP).
-game('0'):- game_2players, fail.
-game('1'):- game_player_bot, fail.
-game('2'):- game_2bots, fail.
-game(_):- !.
+game :- player_select(OP), repeat, game(OP).
+game('0') :- game_2players, fail.
+game('1') :- game_player_bot, fail.
+game('2') :- game_2bots, fail.
+game(_) :- true.
 
-display_game(B, P1, P2):- game_ui(P1, P2), display_board(B).
+display_game(B, P1, P2) :- game_ui(P1, P2), display_board(B).
 
-game_2players:- 
+game_2players :- 
 	get_player(P1),
 	get_player(P2),
-	game_loop_2players(P1,P2,0);
+	start_board(B),
+	game_loop_2players(P1,P2,0,B),
 	wait_enter.
 
-game_player_bot:- 
+% game_player_bot
+game_player_bot :- 
 	board(BB),
 	get_player(Player),
 	display_game(BB, Player, "Bot"),
 	wait_enter.
-
-game_2bots:- 
+% game_2bots
+game_2bots :- 
 	board(BB),
 	display_game(BB, "Bot1", "Bot2"),
 	wait_enter.
 
-% game_loop_2players(P1, P2):- 
-% 	% Player 1 plays
-% 	destroy_board(BL1, BB1, BI1),
-% 	display_game(BL1, P1, P2),
-% 	repeat,
-% 		player_turn(BL1, BB1, BI1, 1),
-% 	% Player 2 plays
[…]

### 2019-11-16 src/menu.pl

@@ -1,4 +1,4 @@
-main_menu(OP):- 
+main_menu(OP) :- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|                  Mbrane                  |'), nl,
@@ -11,7 +11,7 @@ main_menu(OP):-
     write('+------------------------------------------+'), nl,
     get_option('Option: ', OP).
 
-player_select(OP):- 
+player_select(OP) :- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|             Select Game Mode             |'), nl,
@@ -24,7 +24,7 @@ player_select(OP):-
     write('+------------------------------------------+'), nl,
     get_option('Option: ', OP).
 
-instructions_menu:- 
+instructions_menu :- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|               Instructions               |'), nl,
@@ -38,7 +38,7 @@ instructions_menu:-
     write('+------------------------------------------+'), nl,
     wait_enter.
 
-about_menu:- 
+about_menu :- 
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|                   About                  |'), nl,
@@ -54,9 +54,9 @@ about_menu:-
     write('+------------------------------------------+'), nl,
     wait_enter.
 
-game_ui(Player1, Player2):- 
+game_ui(Player1, Player2) :- 
     nl, nl, nl, nl,
-    format('~s~n', [Player1]),
-    format('                 ~p~n', 'VS'),
-    format('~t~s~37|~n', [Player2]).
+    format('   ~s~n', [Player1]),
+    format('                    ~p~n', 'VS'),
+    format('   ~t~s~37|~n', [Player2]).
 

### 2019-11-16 src/util.pl

@@ -1,50 +1,29 @@
 % get_option
 % Option    - return option
-get_option(M, O):- 
-    write(M),
-    get_char(O),
-    get_char(_).
+get_option(M, O) :- write(M), get_char(O), get_char(_).
 
-get_int(M, I):- 
-    write(M),
-    get_code(C),
-    C > 47,
-    C < 58,
-    get_code(10),
-    I is C - 48.
+% get_int
+get_int(M, I) :- write(M), get_code(C), C > 47, C < 58, get_code(10), I is C - 48.
+get_int(M,I) :- write('Invalid number\n'), get_int(M,I).
 
-get_int(M,I) :- 
-    write('Invalid number\n'),
-    get_int(M,I).
+% abs
+abs(N,Abs) :- number(N), N  >= 0, Abs = N.
+abs(N,Abs) :- number(N), N < 0, Abs is -N.
 
-wait_enter:- get_char(_).
+% valid
+valid(N) :- N >= 0, N =< 8.
 
-abs(N,Abs) :- 
-    N  >=  0,
-    Abs = N.
-
-abs(N,Abs) :- 
-    N < 0,
-    Abs is -N.
-
+% get_string
+get_string(String) :- get_code(Ch), get_string_(Ch, [], InvString), reverse(InvString, String).
 get_string_(10, Acc, Acc).
+get_string_(Ch, Acc, String) :- get_code(NCh), get_string_(NCh, [Ch|Acc], String).
 
-get_string_(Ch, Acc, String):- 
-    get_code(NCh),
-    get_string_(NCh, [Ch|Acc], String).
-
-get_string(String):- 
-    get_code(Ch),
-    get_string_(Ch, [], InvString),
-    reverse(InvString, String).
-
-get_player(Player):- 
-	write('Player name'), nl,
-	write('     ?- '),
-	get_string(Player).
+% get_player
+% Player 	- player name
+get_player(Player) :- write('Player name'), nl, write('     ?- '), get_string(Player).
 
 % wait_enter
-wait_enter:- get_char(_).
+wait_enter :- get_char(_).
 
 % replace
 % List      - list to replace
@@ -52,7 +31,7 @@ wait_enter:- get_char(_).
 % Value     - value to replace
 % NewList   - return list
 replace([_|T], 0, V, [V|T]).
[…]

### 2019-11-16 src/board.pl
Next will fix move verification

@@ -78,44 +78,57 @@ update_influence(BI, 8, 7, V, RI) :- update_power(BI, 8, V, RI).
 update_influence(BI, B, N, V, EI) :- update_power(BI, B, V, RI), INF is V/2, update_influence_(RI, B, N, INF, EI).
 
 % update_influence auxiliar
-update_influence_(BI, B, 0, V, EI) :- 
-	B_UP is -3 + B, B_LF is -1 + B, 
-	valid(B_UP), valid(B_LF),
-	update_power(BI, B_UP, V, RI), update_power(RI, B_LF, V, EI).
+update_influence_(BI, B, 0, V, RI) :- 
+	B1 is B - 3, B2 is B - 1, B3 is B - 4,(
+	((B2 = 2; B2 = 5), valid(B1), update_power(BI, B1, V, RI));
+	(valid(B1), valid(B2), update_power(BI, B1, V, CI), update_power(CI, B2, V, DI), update_power(DI, B3, V, RI));
+	(valid(B1), update_power(BI, B1, V, RI));
+	(valid(B2), update_power(BI, B2, V, RI));
+	RI = BI).
 
 update_influence_(BI, B, 1, V, RI) :- 
-	B_UP is -3 + B, 
-	valid(B_UP),
-	update_power(BI, B_UP, V, RI).
+	B1 is B - 3, (
+	valid(B1), update_power(BI, B1, V, RI);
+	RI = BI).
 
-update_influence_(BI, B, 2, V, EI) :- 
-	B_UP is -3 + B, B_RT is B + 1, 
-	valid(B_UP), valid(B_RT),
-	update_power(BI, B_UP, V, RI), update_power(RI, B_RT, V, EI).
+update_influence_(BI, B, 2, V, RI) :- 
+	B1 is B - 3, B2 is B + 1, B3 is B - 2,(
+	((B2 = 3; B2 = 6), valid(B1), update_power(BI, B1, V, RI));
+	(valid(B1), valid(B2), update_power(BI, B1, V, CI), update_power(CI, B2, V, DI), update_power(DI, B3, V, RI));
+	(valid(B1), update_power(BI, B1, V, RI));
+	(valid(B2), update_power(BI, B2, V, RI));
+	RI = BI).
 	
 update_influence_(BI, B, 3, V, RI) :- 
-	B_LF is -1 + B, 
-	valid(B_LF),
-	update_power(BI, B_LF, V, RI).
[…]

### 2019-11-16 src/display.pl

@@ -19,6 +19,4 @@ draw_line([H|T], J) :-
 	draw_line(T, NJ).
 
 
-display_power(P) :- write(' 0 1 2 3 4 5 6 7 8 '),nl,write('|'),display_power_(P).
-display_power_([]) :- nl.
-display_power_([P|T]) :- write(P), write('|'), display_power_(T).
+display_power([B|P]) :- nl,write('Power '),write(P),nl,nl.

### 2019-11-16 src/mbrane.pl

@@ -42,7 +42,9 @@ game_2bots :-
 game_loop_2players(P1, P2, Play, [BL|B]) :- 
 	even(Play),
 	% Player 1 plays
-	display_game(BL, P1, P2),!,
+	display_game(BL, P1, P2),
+	display_power(B),
+	write('Play '), write(Play),nl, !,
 	player_turn([BL|B], 1, [RL|R]),!,
 	% Check complete board
 	incomplete_board(RL),
@@ -52,7 +54,9 @@ game_loop_2players(P1, P2, Play, [BL|B]) :-
 
 game_loop_2players(P1, P2, Play, [BL|B]) :-
 	% Player 2 plays
-	display_game(BL, P1, P2),!,
+	display_game(BL, P1, P2),
+	display_power(B),
+	write('Play '), write(Play),nl, !,
 	player_turn([BL|B], -1, [RL|R]),!,
 	% Check complete board
 	incomplete_board(RL),
@@ -68,6 +72,7 @@ incomplete_board(RL) :-
 % player_turn
 % get player input and make move
 player_turn(B, P, R) :- 
-	get_move(X, Y, V),
+	repeat,
+	get_move(X, Y, V), !,
 	TV is P * V, !,
 	make_move([X, Y], TV, B, R).

### 2019-11-16 src/menu.pl

@@ -1,4 +1,5 @@
 main_menu(OP) :- 
+    cls,
     write('+------------------------------------------+'), nl,
     write('|                                          |'), nl,
     write('|                  Mbrane                  |'), nl,

### 2019-11-16 src/util.pl

@@ -58,3 +58,6 @@ even(N) :- 0 is mod(N,2).
 
 % msg
 msg(M) :- nl,write(M),nl.
+
+% cls
+cls :- write('\e[H\e[2J').

### 2019-11-16 src/board.pl
Read checklist

@@ -29,29 +29,27 @@ board_influence([0, 0, 0, 0, 0, 0, 0, 0, 0]).
 start_board([BL,BB,BI]) :- board(BL), board_blocks(BB), board_influence(BI).
 
 % make_move
-make_move([X, Y], V, [BL, BB, BI], [RL, RB, RI]) :- check_move(X, Y, V, BL, BB), place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
+make_move([X, Y], V, [BL, BB, BI], [RL, RB, RI]) :- place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
 make_move(_, _, _, _) :- msg('error move'), fail.
 
 % check_move
 check_move(X, Y, V, BL, BB) :- 
 	check_x(X), check_y(Y), check_v(V), 
-	check_cell(X, Y, BL), check_restrictions(X, Y, V, BL, BB).
+	check_cell(X, Y, BL), \+ check_restrictions(X, Y, V, BL, BB).
+check_move(_,_,_,_,_) :- write('Invalid move.'),nl,nl,fail.
 
 % check_move auxiliar
 check_x(X) :- valid(X).
 check_y(Y) :- valid(Y).
 check_v(V) :- abs(V,A), valid(A).
 check_cell(X, Y, B) :- nth0(Y, B, L), nth0(X, L, ' ').
-check_restrictions(X, Y, V, BL, BB) :- nl,check_line(8, Y, V, BL), check_column(X, 8, V, BL), coords_to_blocks(X, Y, B, _), check_block(B, 8, V, BB).
-check_line(0, _, _, _) :- true.
-check_line(X, Y, V, BL) :- nth0(Y, BL, L), nth0(X, L, V), fail.
-check_line(X, Y, V, BL) :- NX is -1 + X, check_line(NX, Y, V, BL).
-check_column(_, 0, _, _) :- true.
-check_column(X, Y, V, BL) :- nth0(Y, BL, L), nth0(X, L, V), fail.
-check_column(X, Y, V, BL) :- NY is -1 + Y, check_column(X, NY, V, BL).
-check_block(_, 0, _, _) :- true.
-check_block(B, N, V, BB) :- nth0(B, BB, L), nth0(N, L, V), fail.
-check_block(B, N, V, BB) :- NN is -1 + N, check_block(B, NN, V, BB).
+check_restrictions(X,Y,P,BL,BB) :-
[…]

### 2019-11-16 src/display.pl

@@ -19,4 +19,4 @@ draw_line([H|T], J) :-
 	draw_line(T, NJ).
 
 
-display_power([B|P]) :- nl,write('Power '),write(P),nl,nl.
+display_power(P) :- nl,write('Power '),write(P),nl,nl.

### 2019-11-16 src/mbrane.pl

@@ -39,25 +39,25 @@ game_2bots :-
 	wait_enter.
 
 % game_loop_2players
-game_loop_2players(P1, P2, Play, [BL|B]) :- 
+game_loop_2players(P1, P2, Play, [BL,BB,BI]) :- 
 	even(Play),
 	% Player 1 plays
 	display_game(BL, P1, P2),
-	display_power(B),
+	display_power(BI),
 	write('Play '), write(Play),nl, !,
-	player_turn([BL|B], 1, [RL|R]),!,
+	player_turn([BL,BB,BI], 1, [RL|R]),!,
 	% Check complete board
 	incomplete_board(RL),
 	% Next play
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
 
-game_loop_2players(P1, P2, Play, [BL|B]) :-
+game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	% Player 2 plays
 	display_game(BL, P1, P2),
-	display_power(B),
+	display_power(BI),
 	write('Play '), write(Play),nl, !,
-	player_turn([BL|B], -1, [RL|R]),!,
+	player_turn([BL,BB,BI], -1, [RL|R]),!,
 	% Check complete board
 	incomplete_board(RL),
 	% Next play
@@ -71,8 +71,9 @@ incomplete_board(RL) :-
 
 % player_turn
 % get player input and make move
-player_turn(B, P, R) :- 
+player_turn([BL,BB,BI], P, R) :- 
 	repeat,
-	get_move(X, Y, V), !,
-	TV is P * V, !,
-	make_move([X, Y], TV, B, R).
+	get_move(X, Y, V),
+	TV is P * V,
+	check_move(X, Y, TV, BL, BB),!,
+	make_move([X, Y], TV, [BL,BB,BI], R).

### 2019-11-16 src/util.pl

@@ -3,7 +3,7 @@
 get_option(M, O) :- write(M), get_char(O), get_char(_).
 
 % get_int
-get_int(M, I) :- write(M), get_code(C), C > 47, C < 58, get_code(10), I is C - 48.
+get_int(M, I) :- write(M), get_code(C), C > 47, C < 58, repeat, get_code(10), I is C - 48, !.
 get_int(M,I) :- write('Invalid number\n'), get_int(M,I).
 
 % abs
@@ -61,3 +61,11 @@ msg(M) :- nl,write(M),nl.
 
 % cls
 cls :- write('\e[H\e[2J').
+
+% get_line
+get_line([H|_],0,H):-!.
+get_line([_|T],I,X) :- I1 is I-1, get_line(T,I1,X).
+
+% get_column
+get_column([],_,[]).
+get_column([H|T], I, [R|X]):- get_line(H, I, R), get_column(T,I,X).

### 2019-11-17 src/board.pl
ja tem restricoes

@@ -59,7 +59,7 @@ place_piece(X, Y, V, BL, BB, BI, RL, RB, RI) :-
 	update_influence(BI, B, N, V, RI).
 
 place_piece_board(X, Y, V, BL, RL) :- replace_matrix(BL, X, Y, V, RL).
-place_piece_blocks(B, N, V, BB, RB) :- replace_matrix(BB, B, N, V, RB).
+place_piece_blocks(B, N, V, BB, RB) :- replace_matrix(BB, N, B, V, RB).
 
 % update_influence
 update_influence(BI, _, _, 0, BI) :- true.
@@ -123,7 +123,7 @@ update_influence_(BI, B, 7, V, RI) :-
 update_influence_(BI, B, 8, V, RI) :- 
 	B1 is B + 3, B2 is B + 1, B3 is B + 4,(
 	((B2 = 3; B2 = 6), valid(B1), update_power(BI, B1, V, RI));
-	(write(B1),valid(B1), valid(B2), update_power(BI, B1, V, CI), update_power(CI, B2, V, DI), update_power(DI, B3, V, RI));
+	(valid(B1), valid(B2), update_power(BI, B1, V, CI), update_power(CI, B2, V, DI), update_power(DI, B3, V, RI));
 	(valid(B1), update_power(BI, B1, V, RI));
 	(valid(B2), update_power(BI, B2, V, RI));
 	RI = BI).

### 2019-11-17 src/bot.pl
valid_moves

@@ -1,0 +1,62 @@
+% random_bot
+
+% normal_bot
+
+% smart_bot
+
+% random_move
+
+% valid_moves
+valid_moves([BL,BB], R) :-
+    % check all empty spaces
+    check_all(BL,L),
+    % test all possibilities in empty spaces
+    test_all(L,[BL,BB],R).
+
+
+% check_all
+check_all(B,L) :- check_all_cells(8,8,B,L).
+
+% check_all_cells
+check_all_cells(0, 0, B, [H]) :- check_cell(0, 0, B), H = [0,0].
+check_all_cells(0, 0, _, _) :- true.
+check_all_cells(0, Y, B, [H|T]) :- 
+    check_cell(0, Y, B), H = [0,Y], 
+    NY is Y - 1, check_all_cells(8, NY, B, T).
+check_all_cells(0, Y, B, L) :-
+    NY is Y - 1, check_all_cells(8, NY, B, L).
+check_all_cells(X, Y, B, [H|T]) :-
+    check_cell(X, Y, B), H = [X,Y], 
+    NX is X - 1, check_all_cells(NX, Y, B, T).
+check_all_cells(X, Y, B, L) :- 
+    NX is X - 1, check_all_cells(NX, Y, B, L).
+
+% test_all
+test_all(I, B, R) :- test_all_cells(8, I, B, R).
+
+% test_all_cells
+test_all_cells(0, [[X,Y]], [BL,BB], [H]) :-
+    check_move(X, Y, 0, BL, BB), H = [X,Y,0].
+
+test_all_cells(0, [_], _, _) :- true.
+
+test_all_cells(0, [[X,Y]|T], [BL,BB], [H|R]) :-
+    check_move(X, Y, 0, BL, BB),
+    H = [X,Y,0],
+    test_all_cells(8, T, [BL,BB], R).
+
+test_all_cells(0, T, [BL,BB], R) :-
+    test_all_cells(8, T, [BL,BB], R).
+
+test_all_cells(V, [[X,Y]|T], [BL,BB], [H|R]) :-
+    check_move(X, Y, V, BL, BB),
+    H = [X,Y,V],
+    NV is V - 1, 
+    test_all_cells(NV, [[X,Y]|T], [BL,BB], R).
+
+test_all_cells(V, I, [BL,BB], R) :-
+    NV is V - 1,
+    test_all_cells(NV, I, [BL,BB], R).
+
+% get_best_move
+

### 2019-11-17 src/mbrane.pl

@@ -4,6 +4,7 @@
  :- include('menu.pl').
  :- include('board.pl').
  :- include('display.pl').
+ :- include('bot.pl').
 
 mbrane :- main_menu(OP), repeat, mbrane(OP).
 mbrane('0') :- game, fail.
@@ -19,6 +20,7 @@ game(_) :- true.
 
 display_game(B, P1, P2) :- game_ui(P1, P2), display_board(B).
 
+% game_2players
 game_2players :- 
 	get_player(P1),
 	get_player(P2),
@@ -32,6 +34,7 @@ game_player_bot :-
 	get_player(Player),
 	display_game(BB, Player, "Bot"),
 	wait_enter.
+
 % game_2bots
 game_2bots :- 
 	board(BB),

### 2019-11-17 src/board.pl
changed report

@@ -28,9 +28,9 @@ board_influence([0, 0, 0, 0, 0, 0, 0, 0, 0]).
 % get starting boards
 start_board([BL,BB,BI]) :- board(BL), board_blocks(BB), board_influence(BI).
 
-% make_move
-make_move([X, Y], V, [BL, BB, BI], [RL, RB, RI]) :- place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
-make_move(_, _, _, _) :- msg('error move'), fail.
+% move
+move([X, Y, V], [BL, BB, BI], [RL, RB, RI]) :- place_piece(X, Y, V, BL, BB, BI, RL, RB, RI).
+move(_, _, _, _) :- msg('error move'), fail.
 
 % check_move
 check_move(X, Y, V, BL, BB) :- 

### 2019-11-17 src/bot.pl

@@ -33,13 +33,11 @@ check_all_cells(X, Y, B, L) :-
 
 % test_all
 test_all(I, B, R) :- test_all_cells(8, I, B, R).
-
 % test_all_cells
 test_all_cells(0, [[X,Y]], [BL,BB], [H]) :-
     check_move(X, Y, 0, BL, BB), H = [X,Y,0].
 
 test_all_cells(0, [_], _, _) :- true.
-
 test_all_cells(0, [[X,Y]|T], [BL,BB], [H|R]) :-
     check_move(X, Y, 0, BL, BB),
     H = [X,Y,0],

### 2019-11-17 src/mbrane.pl

@@ -79,4 +79,4 @@ player_turn([BL,BB,BI], P, R) :-
 	get_move(X, Y, V),
 	TV is P * V,
 	check_move(X, Y, TV, BL, BB),!,
-	make_move([X, Y], TV, [BL,BB,BI], R).
+	move([X, Y, TV], [BL,BB,BI], R).

### 2019-11-17 src/mbrane.pl
game_over

@@ -50,7 +50,7 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], 1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
+	game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
@@ -62,15 +62,16 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], -1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
+	game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
 
-% incomplete_board
-% true if board incomplete
-incomplete_board(RL) :- 
-	true.
+% game_over
+game_over([B|BI],W) :- 
+	valid_moves(B, R),
+	R = [],
+	get_winner(BI,W).
 
 % player_turn
 % get player input and make move

### 2019-11-17 src/board.pl
Random bot working yeeeeey

@@ -36,7 +36,7 @@ make_move(_, _, _, _) :- msg('error move'), fail.
 check_move(X, Y, V, BL, BB) :- 
 	check_x(X), check_y(Y), check_v(V), 
 	check_cell(X, Y, BL), \+ check_restrictions(X, Y, V, BL, BB).
-check_move(_,_,_,_,_) :- write('Invalid move.'),nl,nl,fail.
+check_move(_,_,_,_,_) :- fail.
 
 % check_move auxiliar
 check_x(X) :- valid(X).

### 2019-11-17 src/bot.pl

@@ -1,10 +1,16 @@
-% random_bot
-
 % normal_bot
 
 % smart_bot
 
 % random_move
+% get a random move for a bot
+random_move([BL,BB], X, Y, V) :-
+    %get the random move
+    valid_moves([BL,BB],R),
+    length(R, Len),
+    random(0,Len,Rand),
+    nth0(Rand, R, [X,Y,V]).
+
 
 % valid_moves
 valid_moves([BL,BB], R) :-
@@ -19,44 +25,46 @@ check_all(B,L) :- check_all_cells(8,8,B,L).
 
 % check_all_cells
 check_all_cells(0, 0, B, [H]) :- check_cell(0, 0, B), H = [0,0].
-check_all_cells(0, 0, _, _) :- true.
+
 check_all_cells(0, Y, B, [H|T]) :- 
     check_cell(0, Y, B), H = [0,Y], 
     NY is Y - 1, check_all_cells(8, NY, B, T).
+
 check_all_cells(0, Y, B, L) :-
     NY is Y - 1, check_all_cells(8, NY, B, L).
+
+check_all_cells(0, 0, _, _) :- true.
+
 check_all_cells(X, Y, B, [H|T]) :-
     check_cell(X, Y, B), H = [X,Y], 
     NX is X - 1, check_all_cells(NX, Y, B, T).
+
 check_all_cells(X, Y, B, L) :- 
     NX is X - 1, check_all_cells(NX, Y, B, L).
 
 % test_all
-test_all(I, B, R) :- test_all_cells(8, I, B, R).
+test_all(I, B, R) :- test_all_cells(8, I, B, Acc, R).
 
-% test_all_cells
-test_all_cells(0, [[X,Y]], [BL,BB], [H]) :-
-    check_move(X, Y, 0, BL, BB), H = [X,Y,0].
 
-test_all_cells(0, [_], _, _) :- true.
+test_all_cells(0,[], [BL,BB], Acc, Acc).
 
-test_all_cells(0, [[X,Y]|T], [BL,BB], [H|R]) :-
-    check_move(X, Y, 0, BL, BB),
-    H = [X,Y,0],
-    test_all_cells(8, T, [BL,BB], R).
+test_all_cells(0, [[X,Y]|T], [BL,BB], Acc, R) :-
+    check_move(X, Y, V, BL, BB),
+    H = [X,Y,V],
[…]

### 2019-11-17 src/mbrane.pl

@@ -1,4 +1,5 @@
  :- use_module(library(lists)).
+ :- use_module(library(random)). 
 
  :- include('util.pl').
  :- include('menu.pl').
@@ -30,15 +31,15 @@ game_2players :-
 
 % game_player_bot
 game_player_bot :- 
-	board(BB),
 	get_player(Player),
-	display_game(BB, Player, "Bot"),
+	start_board(B),
+	game_loop_player_bot(Player,"Bot",0,B),
 	wait_enter.
 
 % game_2bots
 game_2bots :- 
-	board(BB),
-	display_game(BB, "Bot1", "Bot2"),
+	start_board(B),
+	game_loop_2_bots("Bot1","Bot2",0,B),
 	wait_enter.
 
 % game_loop_2players
@@ -67,6 +68,62 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
 
+game_loop_player_bot(P1,P2,Play,[BL,BB,BI]) :-
+	even(Play),
+	% Player 1 plays
+	display_game(BL, P1, P2),
+	display_power(BI),
+	write('Play '), write(Play),nl, !,
+	player_turn([BL,BB,BI], 1, [RL|R]),!,
+	% Check complete board
+	incomplete_board(RL),
+	% Next play
+	NextPlay is Play + 1,
+	game_loop_player_bot(P1,P2,NextPlay,[RL|R]).
+
+
+game_loop_player_bot(P1,P2,Play,[BL,BB,BI]) :-
+	% Bot plays
+	display_game(BL, P1, P2),
+	display_power(BI),
+	write('Play '), write(Play),nl, !,
+	bot_turn([BL,BB,BI], -1, [RL|R]),!,
+	% Check complete board
+	incomplete_board(RL),
+	% Next play
+	NextPlay is Play + 1,
+	game_loop_player_bot(P1,P2,NextPlay,[RL|R]).
+
+
+game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
+	%Bot1 plays
+	even(Play),
+	% Player 1 plays
+	display_game(BL, P1, P2),
+	display_power(BI),
+	write('Play '), write(Play),nl, !,
+	bot_turn([BL,BB,BI], 1, [RL|R]),!,
+	% Check complete board
[…]

### 2019-11-17 src/mbrane.pl
get_winner and game_over

@@ -73,6 +73,19 @@ game_over([B|BI],W) :-
 	R = [],
 	get_winner(BI,W).
 
+% get_winner
+get_winner(B,W) :-
+	get_winner_(B,P1,P2),
+	(P1 > P2, W is 1); W is -1.
+
+get_winner_([],P1,P2) :- P1 is 0, P2 is 0.
+get_winner_([H|T],P1,P2):-
+	get_winner_(T,N1,N2),
+	((H > 0, P1 is N1 + 1, P2 is N2);
+		(H < 0, P1 is N1, P2 is N2 + 1)).
+	
+	
+
 % player_turn
 % get player input and make move
 player_turn([BL,BB,BI], P, R) :- 

### 2019-11-17 src/bot.pl
stable state

@@ -6,10 +6,15 @@
 % get a random move for a bot
 random_move([BL,BB], X, Y, V) :-
     %get the random move
-    valid_moves([BL,BB],R),
+    valid_moves([BL,BB],R), !,
     length(R, Len),
     random(0,Len,Rand),
     nth0(Rand, R, [X,Y,V]).
+
+random_move(random_move([BL,BB], _, _, _)) :-
+    valid_moves([BL,BB],R), !,
+    R = [],
+    fail.
 
 
 % valid_moves
@@ -21,36 +26,42 @@ valid_moves([BL,BB], R) :-
 
 
 % check_all
-check_all(B,L) :- check_all_cells(8,8,B,L).
+check_all(B,L) :- check_all_cells(8,8,B,[],L),write(L).
 
-% check_all_cells
-check_all_cells(0, 0, B, [H]) :- check_cell(0, 0, B), H = [0,0].
+check_all_cells(0, 0, B, [[0,0]|Acc], [0,0]|Acc]) :-
+    check_cell(0,0,B).
 
-check_all_cells(0, Y, B, [H|T]) :- 
-    check_cell(0, Y, B), H = [0,Y], 
-    NY is Y - 1, check_all_cells(8, NY, B, T).
+check_all_cells(0, 0, B, Acc, Acc).
 
-check_all_cells(0, Y, B, L) :-
-    NY is Y - 1, check_all_cells(8, NY, B, L).
+check_all_cells(0, Y, B, Acc, L) :-
+    check_cell(X, Y, B),
+    H = [0,Y],
+    NY is Y - 1,
+    check_all_cells(8,NY, B, [H|Acc], L).
 
-check_all_cells(0, 0, _, _) :- true.
+check_all_cells(0, Y, B, Acc, L) :-
+    NY is Y - 1,
+    check_all_cells(8,NY, B, [H|Acc], L).
 
-check_all_cells(X, Y, B, [H|T]) :-
-    check_cell(X, Y, B), H = [X,Y], 
-    NX is X - 1, check_all_cells(NX, Y, B, T).
+check_all_cells(X, Y, B, Acc, L) :-
+    check_cell(X, Y, B),
+    H = [X,Y],
+    NX is X - 1,
+    check_all_cells(NX,Y,B,[H|Acc],L).
 
-check_all_cells(X, Y, B, L) :- 
[…]

### 2019-11-17 src/mbrane.pl

@@ -39,7 +39,7 @@ game_player_bot :-
 % game_2bots
 game_2bots :- 
 	start_board(B),
-	game_loop_2_bots("Bot1","Bot2",0,B),
+	game_loop_2bots("Bot1","Bot2",0,B),
 	wait_enter.
 
 % game_loop_2players
@@ -51,7 +51,7 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], 1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
+	game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
@@ -63,7 +63,7 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], -1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
+	game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
 	game_loop_2players(P1,P2,NextPlay,[RL|R]).
@@ -128,20 +128,38 @@ game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
 % true if board incomplete
 incomplete_board(RL) :- 
 	true.
+% game_over
+game_over([B|BI],W) :- 
+	valid_moves(B, R),
+	R = [],
+	get_winner(BI,W).
+
+% get_winner
+get_winner(B,W) :-
+	get_winner_(B,P1,P2),
+	(P1 > P2, W is 1); W is -1.
+
+get_winner_([],P1,P2) :- P1 is 0, P2 is 0.
+get_winner_([H|T],P1,P2):-
+	get_winner_(T,N1,N2),
+	((H > 0, P1 is N1 + 1, P2 is N2);
+		(H < 0, P1 is N1, P2 is N2 + 1)).
+	
+	
 
 % player_turn
 % get player input and make move
 player_turn([BL,BB,BI], P, R) :- 
-	repeat,
 	get_move(X, Y, V),
 	TV is P * V,
-	check_move(X, Y, TV, BL, BB),!,
+	move([X, Y], TV, [BL,BB,BI], R).
+
+bot_turn([BL,BB,BI], P, R) :-
[…]

### 2019-11-17 src/bot.pl
Almost now

@@ -26,7 +26,7 @@ valid_moves([BL,BB], R) :-
 
 
 % check_all
-check_all(B,L) :- check_all_cells(8,8,B,[],L),write(L).
+check_all(B,L) :- check_all_cells(8,8,B,[],L).
 
 check_all_cells(0, 0, B, [[0,0]|Acc], [0,0]|Acc]) :-
     check_cell(0,0,B).
@@ -54,7 +54,7 @@ check_all_cells(X, Y, B, Acc ,L) :-
     check_all_cells(NX,Y,B,Acc,L).
 
 % test_all
-test_all(I, B, R) :- test_all_cells(8, I, B, [], R), write(R).
+test_all(I, B, R) :- test_all_cells(8, I, B, [], R).
 
 
 test_all_cells(_,[], [BL,BB], Acc, Acc).

### 2019-11-17 src/mbrane.pl

@@ -104,32 +104,38 @@ game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	bot_turn([BL,BB,BI], 1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
-	% Next play
-	NextPlay is Play + 1,
-	game_loop_2bots(P1,P2,NextPlay,[RL|R]).
+	(
+		\+game_over([B,BI],_),
+		% Next play
+		NextPlay is Play + 1,
+		game_loop_2bots(P1,P2,NextPlay,[RL|R]);
+		game_over([B,BI],W),
+		write('The winner is'),
+		write(W)
+	).
 
 
 game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
-	% Bot plays
+	% Bot 2 plays
 	display_game(BL, P1, P2),
 	display_power(BI),
 	write('Play '), write(Play),nl, !,
 	bot_turn([BL,BB,BI], -1, [RL|R]),!,
 	% Check complete board
-	incomplete_board(RL),
-	% Next play
-	NextPlay is Play + 1,
-	game_loop_2bots(P1,P2,NextPlay,[RL|R]).
+	(
+		\+game_over([B,BI],_),
+		% Next play
+		NextPlay is Play + 1,
+		write(lol),
+		game_loop_2bots(P1,P2,NextPlay,[RL|R]);
+		game_over([B,BI],W),
+		write('The winner is'),
+		write(W)
+	).
 
 
-
-% incomplete_board
-% true if board incomplete
-incomplete_board(RL) :- 
-	true.
 % game_over
-game_over([B|BI],W) :- 
+game_over([B,BI],W) :- 
 	valid_moves(B, R),
 	R = [],
 	get_winner(BI,W).

### 2019-11-17 docs/report_latex/template.tex

@@
 
-Descrever o projeto e implementação da lógica do jogo em Prolog, incluindo a forma de representação do estado do tabuleiro e sua visualização, execução de movimentos, verificação do cumprimento das regras do jogo, determinação do final do jogo e cálculo das jogadas a realizar pelo computador utilizando diversos níveis de jogo.
-Sugere-se a estruturação desta secção da seguinte forma:
-
 % TODO complete
@@
 \subsection{Board viewing} 
-Descrever a interface com o utilizador, descrevendo a visualização do estado do jogo (pode ser idêntico ao descrito no relatório intercalar) e robustez da interface/validações de entrada.
+Before each move, the board is displayed on the screen.
+To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}.
+This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself.
+The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.
 
@@
 \subsection{List valid plays} 
-Obtenção de uma lista de jogadas possíveis. O predicado deve chamar-se \textit{valid\_moves(+Board, +Player, -ListOfMoves)}.
+As per requested, we developed a predicate that returns a list of all possible moves.
+This predicate is \textit{valid\_moves(+Board, -R)}.
+The first argument of the predicate is a list with the board of lines and board of blocks.
+This predicate works by first finding a list of all empty cells with \textit{check\_all(+Board, -List),}.
+Then it tests all possible values in those cells with \textit{test_all(+List, +Board, +Result)}.
 
@@
 \subsection{Play execution} 
-Validação e execução de uma jogada num tabuleiro, obtendo o novo estado do jogo. O predicado deve chamar-se \textit{move(+Move, +Board, -NewBoard)}.
+Each player can make a move per turn \textit{player\_turn(+Board, +Player, -NewBoard)}.
+In this turn predicate, the program asks the player what he wants to play with \textit{get_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
+If the move is invalid the program repeats the previous action, otherwise, it returns a new board with the new piece.
 

### 2019-11-17 docs/report_latex/template.tex
commenting

@@
 
-% TODO
 \section*{Summary}
-Resumo do trabalho (aprox. 250 palavras) descrevendo sucintamente o problema abordado, objetivos, metodologia usada na sua resolução, principais resultados e conclusões).
 
-\paragraph{} 
 The goal of this project was to program a board game using the prolog language. In our case the game in question is Mbrane, a 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-% TODO complete
 \section{Introduction}
@@
 
-% TODO complete
 \subsection{Game state representation} 
@@
 
-% TODO complete
 \subsection{Board viewing} 
@@
 
-% TODO complete
 \subsection{List valid plays} 
@@
 
-% TODO complete
 \subsection{Play execution} 
@@
 
-% TODO complete
 \subsection{Game finalization} 
-Verificação do fim do jogo, com identificação do vencedor. O predicado deve chamar-se \textit{game\_over(+Board, -Winner)}.
-
-\paragraph{}
-The game is in the final state if no more numbers can be placed on the board. When this happens the game enters the 
-\textbf{Resolution Phase} and proceds to make the calculartions mentioned in \textbf{Section 2}. Then the winner (if it exists) is
-announced.
+For the end of game we need to verify if there are any possible moves left.
+This is done by predicate \textit{game\_over(+Board, -Winner)}.
+If there are any moves left, it fails and the game continues.
+Otherwise it will find out who won the game. This is done by verifying which player controls the most blocks in the predicate \textit{get\_winner(+Board, -Winner)}.
 
@@
 \section{Conclusions}
-Que conclui deste projecto? Como poderia melhorar o trabalho desenvolvido?
+With this work we have developed our way of thinking in a new way. Although Prolog can be compared to other programming languages, it is unique in the way it works.
+The biggest problem we found was trying to make use of dynamic predicates to create a sort of global board. After testing a lot we decided to give up on the idea.
+In terms of the game mechanics, there are a lot of verifications
 

### 2019-11-17 src/board.pl

@@ -1,3 +1,8 @@
+/*	PLOG 2019/2020
+ *	Leonardo Moura & Joao Campos
+ *	File responsible for interaction with the board
+ */
+
 % starting board list of lines
 board([
 	[' ', ' ', ' ', ' ', ' ', ' ', ' ', ' ', ' '],

### 2019-11-17 src/bot.pl

@@ -1,23 +1,26 @@
-% random_bot
+/*	PLOG 2019/2020
+ *	Leonardo Moura & Joao Campos
+ *	File for generating moves using different strategies
+ */
 
-% normal_bot
+% TODO random_bot
 
-% smart_bot
+% TODO normal_bot
 
-% random_move
+% TODO  smart_bot
 
-% valid_moves
+% TODO random_move
+
+% valid_moves(+Board, -Result)
 valid_moves([BL,BB], R) :-
-    % check all empty spaces
     check_all(BL,L),
-    % test all possibilities in empty spaces
     test_all(L,[BL,BB],R).
 
 
-% check_all
+% check_all(+Board, -List)
 check_all(B,L) :- check_all_cells(8,8,B,L).
 
-% check_all_cells
+% check_all_cells(+X, +Y, +Board, -List)
 check_all_cells(0, 0, B, [H]) :- check_cell(0, 0, B), H = [0,0].
 check_all_cells(0, 0, _, _) :- true.
 check_all_cells(0, Y, B, [H|T]) :- 
@@ -31,9 +34,10 @@ check_all_cells(X, Y, B, [H|T]) :-
 check_all_cells(X, Y, B, L) :- 
     NX is X - 1, check_all_cells(NX, Y, B, L).
 
-% test_all
+% test_all(+Input, +Board, -Result)
 test_all(I, B, R) :- test_all_cells(8, I, B, R).
-% test_all_cells
+
+% test_all_cells(+Value, +Coords, +Board, -Result)
 test_all_cells(0, [[X,Y]], [BL,BB], [H]) :-
     check_move(X, Y, 0, BL, BB), H = [X,Y,0].
 
@@ -56,5 +60,5 @@ test_all_cells(V, I, [BL,BB], R) :-
     NV is V - 1,
     test_all_cells(NV, I, [BL,BB], R).
 
-% get_best_move
+% TODO get_best_move
 

### 2019-11-17 src/mbrane.pl

@@ -1,3 +1,8 @@
+/*	PLOG 2019/2020
+ *	Leonardo Moura & Joao Campos
+ *	Main file of project
+ */
+ 
  :- use_module(library(lists)).
 
  :- include('util.pl').
@@ -6,7 +11,7 @@
  :- include('display.pl').
  :- include('bot.pl').
 
-mbrane :- main_menu(OP), repeat, mbrane(OP).
+play :- main_menu(OP), repeat, mbrane(OP).
 mbrane('0') :- game, fail.
 mbrane('1') :- instructions_menu, fail.
 mbrane('2') :- about_menu, fail.
@@ -17,8 +22,6 @@ game('0') :- game_2players, fail.
 game('1') :- game_player_bot, fail.
 game('2') :- game_2bots, fail.
 game(_) :- true.
-
-display_game(B, P1, P2) :- game_ui(P1, P2), display_board(B).
 
 % game_2players
 game_2players :- 
@@ -50,10 +53,11 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], 1, [RL|R]),!,
 	% Check complete board
-	game_over([BL,BB,BI],W),
+	(\+game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
-	game_loop_2players(P1,P2,NextPlay,[RL|R]).
+	game_loop_2players(P1,P2,NextPlay,[RL|R]));
+		display_win(BL, P1, P2).
 
 game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	% Player 2 plays
@@ -62,10 +66,11 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 	write('Play '), write(Play),nl, !,
 	player_turn([BL,BB,BI], -1, [RL|R]),!,
 	% Check complete board
-	game_over([BL,BB,BI],W),
+	(\+game_over([BL,BB,BI],W),
 	% Next play
 	NextPlay is Play + 1,
-	game_loop_2players(P1,P2,NextPlay,[RL|R]).
+	game_loop_2players(P1,P2,NextPlay,[RL|R]));
+		display_win(BL, P1, P2).
 
 % game_over
 game_over([B|BI],W) :- 

### 2019-11-17 src/util.pl

@@ -1,5 +1,9 @@
-% get_option
-% Option    - return option
+/*	PLOG 2019/2020
+ *	Leonardo Moura & Joao Campos
+ *	File with generic function used in the code
+ */
+
+% get_option(+Message, -Option)
 get_option(M, O) :- write(M), get_char(O), get_char(_).
 
 % get_int

### 2019-11-17 docs/report_latex/template.tex
Final report

--- 2019-11-17 docs/report_latex/template.tex
@@
 \paragraph{}
-This project was developed during the Logic Programing Course in the context of the third the Integrated Masters in Informatics 
-and Computing Engineering. The goal is to implement in Prolog a board game, in this case \textit{Mbrane}.
+This project was developed during the Logic Programing Course in the context of the third year of the Integrated Masters in Informatics 
+and Computing Engineering at FEUP. The goal was to implement the logic of a board game in Prolog, in this case \textit{Mbrane}.
+
+\paragraph{}
+Here is a short explanation of all the sections in this report:
+
+\begin{itemize}
+    \item \textbf{Game presentation:} Clarification of the most relevant aspets of the game, both it's rules and origin.
+    \begin{itemize}
+        \item \textbf{Origin:} Description the origin of the game, and it was based on the journals of the game
+        creator himself.
+        \item \textbf{Rules:} Description of all the rules of the game. 
+    \end{itemize}
+
+    \item \textbf{Game Logic:} Description of the game logic and how it was implememted in Prolog, it focuses
+    on the most relevant predicates.
+    \begin{itemize}
+        \item \textbf{Game state representation:} Description of how all the different states of the game are represented internally in Prolog. 
+        \item \textbf{Board viewing:} Description of how we use the internal game state representation to display the game in a relatively user friendly way, using a text interface.
+        \item \textbf{List valid plays:} Description of how the we are able to determine if a play is valid or not, and more importantly, how we can find all the plays that can be made in a given moment.
+        \item \textbf{Game finalization:} Description of how we are able to detect the game is in a final state in order to determine the winner.
+        \item \textbf{Board Evaliation:} Description of how we can evaluate the board, in order to find if a given play is valid or not.
+        \item \textbf{Plays of the computer:} Description of the computer choses a move when given a list of possible moves.
+    \end{itemize}
+\end{itemize}
 
@@
 
-% TODO complete
 \subsection{Game state representation} 
 Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
-boards represented in the game’s data structures. There’s a board predicate that represents the game board itself, a
+boards represented in the game’s data structures. There’s a board predicate that represents the game \textbf{board} itself, a
 list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
@@
 power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
-updated accordingly.
+updated accordingly. The predicate used to declare a fresh board is \textit{start\_board(-Board)}, which unifies a variable to a list 
+of containing the three boards mentioned above. In order to distinguish both players we determined that Player1 would place 
+positive numbers on the board, and Player2 would place negative numbers. This eases the calculations and makes it possible 
+to display to the user the which player has controll in each block of the board
 
-% TODO complete
+\begin{center}
+    \includegraphics[scale=0.3]{img/board.png}
+\end{center}
+
 \subsection{Board viewing} 
@@
 The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.
+The power of all the blocks is also displayed usinf \textit{display\_power(+Power)}
 
-% TODO complete
+\begin{center}
+    \includegraphics[scale=0.3]{img/display.png}
+\end{center}
+
 \subsection{List valid plays} 
@@
 This predicate works by first finding a list of all empty cells with \textit{check\_all(+Board, -List),}.
-Then it tests all possible values in those cells with \textit{test_all(+List, +Board, +Result)}.
+Then it tests all possible values in those cells with \textit{test\_all(+List, +Board, +Result)}.
+\textit{R} is a list of all the possible moves which are also lists in the format \textit{[X,Y,Value]}.
 
-% TODO complete
+\begin{center}
+    \includegraphics[scale=0.4]{img/test_all.png}
+\end{center}
+
 \subsection{Play execution} 
 Each player can make a move per turn \textit{player\_turn(+Board, +Player, -NewBoard)}.
-In this turn predicate, the program asks the player what he wants to play with \textit{get_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
+In this turn predicate, the program asks the player what he wants to play with \textit{get\_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
 If the move is invalid the program repeats the previous action, otherwise, it returns a new board with the new piece.
 
+\begin{center}
+    \includegraphics[scale=0.4]{img/player_turn.png}
+\end{center}
+
+\pagebreak
+\subsection{Game finalization}
+
+\paragraph{}
+The game is in the final state if no more numbers can be placed on the board, according to placing rule already 
+mentioned. We know this usinf the \textit{valid\_moves(+Board, -R)}. If it the Result list is empty, then no more valid
+moves can be made, which means the game is in the final state. When this happens the \textit{game\_over(+Board, -Winner)}
+predicate calculates the winner of the game.
+
+\begin{center}
+    \includegraphics[scale=0.4]{img/game_over.png}
+\end{center}
+
+\subsection{Board evaluation}
 \paragraph{}
@@
 
-% TODO complete
-\subsection{Game finalization} 
-Verificação do fim do jogo, com identificação do vencedor. O predicado deve chamar-se \textit{game\_over(+Board, -Winner)}.
+\paragraph{}
+We evaluate if a play is possible using the \textit{check\_move(+X,+Y,+Value,+BL,+BB)}, it calculates if the move is possible using 
+all the restrictions merntioned  above, if some of those restrictions are not met the predicate fails indicating the move can't be made.
 
-\paragraph{}
-The game is in the final state if no more numbers can be placed on the board. When this happens the game enters the 
-\textbf{Resolution Phase} and proceds to make the calculartions mentioned in \textbf{Section 2}. Then the winner (if it exists) is
-announced.
-
-% TODO complete
-\subsection{Board evaluation}
-Avaliação do estado do jogo, que permitirá comparar a aplicação das diversas jogadas disponíveis. O predicado deve chamar-se \textit{value(+Board, +Player, -Value)}.
+\begin{center}
+    \includegraphics[scale=0.4]{img/check_move.png}
+\end{center}
 
@@
 \subsection{Plays of the computer} 
-Escolha da jogada a efetuar pelo computador, dependendo do nível de dificuldade. O predicado deve chamar-se \textit{choose\_move(+Board, +Level, -Move)}.
+The computer plays only in an easy difficulty setting, this means that for each turn of the computer we get all the possible plays using 
+the \textit{valid\_moves(+Board, -R)} predicate. Then using the \textit{random/3} predicate from the SicStus random library we chose a random 
+move and execute it. The predicate that makes the move move of the computer is \textit{bot\_turn(+Board,+Power,-Result)}.
+
+\begin{center}
+    \includegraphics[scale=0.4]{img/bot_move.png}
+\end{center}
 
@@
 \pagebreak
-% TODO complete
 \section{Conclusions}
-Que conclui deste projecto? Como poderia melhorar o trabalho desenvolvido?
+
+\paragraph{}
+Overall, the project was a really good way to practice the Prolog programming language, and
+also see how it can be used to create a real application (in this case a game). In the 
+begginning we really struggled to understand the implications of the language and how 
+we could use it to build a game. The total change of paradigm from what we were used to 
+was really tough and the learning curve was a really rough one. Our start was very slow 
+and we took some time before we could start working at a decent pace.
+
+\paragraph{}
+We had a lot of trouble during the development of the project. Everything started on our first
+approach to internally store and use the game board. Only when we were trying to make 
+the game "playable" did we realize our approach was not the best one, as we were not finding a 
+way to make the game play past the second round. This required an almost total refactoring of
+the code which made us loose a lot of time. We ended up not having time to implement a more 
+difficult game mode agains the computer using a little aritifitial inteligence wich was 
+something we were looking forward to do. Due to these time issues we also ended up not implementing
+the final \textit{Resolution Phase}. We made this decision having in mind it whould not add much complexity
+to the project as it is only a bunch of calculations.
+
+\paragraph{}
+In the end of the development of the project we actually were programming at a good rythm. So 
+we find this was a positive experience, that helped us getting a better understanding 
+of declarative programming languages and logic programming.
 

### 2019-11-17 src/mbrane.pl

@@ -164,7 +164,6 @@ player_turn([BL,BB,BI], P, R) :-
 bot_turn([BL,BB,BI], P, R) :-
 	random_move([BL,BB],X,Y,V),
 	TV is P * V,
-	write(X), write(Y), write(TV),
 	make_move([X, Y], TV, [BL,BB,BI], R).
 
 bot_turn([BL,BB,BI], P, R) :-

### 2019-11-18 docs/report_latex/template.tex
Fixed report and 2 bot bug

@@
 \subsection{Game state representation} 
-Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
+Although the user can only see one board at a time, in a any phase of the game, there are actually three
 boards represented in the game’s data structures. There’s a board predicate that represents the game \textbf{board} itself, a
@@
 The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.
-The power of all the blocks is also displayed usinf \textit{display\_power(+Power)}
+The power of all the blocks is also displayed using\textit{display\_power(+Power)}
 
@@
 The game is in the final state if no more numbers can be placed on the board, according to placing rule already 
-mentioned. We know this usinf the \textit{valid\_moves(+Board, -R)}. If it the Result list is empty, then no more valid
+mentioned. We know this using the \textit{valid\_moves(+Board, -R)}. If the Result list is empty, then no more valid
 moves can be made, which means the game is in the final state. When this happens the \textit{game\_over(+Board, -Winner)}

### 2019-11-18 src/bot.pl

@@ -19,7 +19,7 @@ valid_moves([BL,BB], R) :-
 
 
 % check_all
-check_all(B,L) :- check_all_cells(8,8,B,[],L).
+check_all(B,L) :- check_all_cells(8,8,B,[],L),write(L).
 
 check_all_cells(0, 0, B, [[0,0]|Acc], [[0,0]|Acc]) :-
     check_cell(0,0,B).
@@ -34,7 +34,7 @@ check_all_cells(0, Y, B, Acc, L) :-
 
 check_all_cells(0, Y, B, Acc, L) :-
     NY is Y - 1,
-    check_all_cells(8,NY, B, [_|Acc], L).
+    check_all_cells(8,NY, B, Acc, L).
 
 check_all_cells(X, Y, B, Acc, L) :-
     check_cell(X, Y, B),
@@ -47,7 +47,7 @@ check_all_cells(X, Y, B, Acc ,L) :-
     check_all_cells(NX,Y,B,Acc,L).
 
 % test_all
-test_all(I, B, R) :- test_all_cells(8, I, B, [], R).
+test_all(I, B, R) :- test_all_cells(8, I, B, [], R),write(R).
 
 
 test_all_cells(_,[], _, Acc, Acc).

### 2019-11-18 docs/report_latex/template.tex
Final version

@@
 The computer plays only in an easy difficulty setting, this means that for each turn of the computer we get all the possible plays using 
-the \textit{valid\_moves(+Board, -R)} predicate. Then using the \textit{random/3} predicate from the SicStus random library we chose a random 
+the \textit{valid\_moves(+Board, -R)} predicate. Then using the \textit{random/3} predicate from the SicStus random library, we choose a random 
 move and execute it. The predicate that makes the move move of the computer is \textit{bot\_turn(+Board,+Power,-Result)}.
@@
 the code which made us loose a lot of time. We ended up not having time to implement a more 
-difficult game mode agains the computer using a little aritifitial inteligence wich was 
+difficult game mode agains the computer using a little aritifitial inteligence which was 
 something we were looking forward to do. Due to these time issues we also ended up not implementing
-the final \textit{Resolution Phase}. We made this decision having in mind it whould not add much complexity
-to the project as it is only a bunch of calculations.
+the final \textit{Resolution Phase}. We made this decision having in mind it whould not add much
+ complexity to the project as it would only involve some calculations using already existing preicates.
 

### 2019-11-18 src/bot.pl
I really think i'm done now

@@ -19,7 +19,7 @@ valid_moves([BL,BB], R) :-
 
 
 % check_all
-check_all(B,L) :- check_all_cells(8,8,B,[],L),write(L).
+check_all(B,L) :- check_all_cells(8,8,B,[],L).
 
 check_all_cells(0, 0, B, [[0,0]|Acc], [[0,0]|Acc]) :-
     check_cell(0,0,B).
@@ -47,7 +47,7 @@ check_all_cells(X, Y, B, Acc ,L) :-
     check_all_cells(NX,Y,B,Acc,L).
 
 % test_all
-test_all(I, B, R) :- test_all_cells(8, I, B, [], R),write(R).
+test_all(I, B, R) :- test_all_cells(8, I, B, [], R).
 
 
 test_all_cells(_,[], _, Acc, Acc).

### 2019-11-18 src/mbrane.pl

@@ -57,7 +57,7 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 		game_loop_2players(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
+		(W = -1, format('~s~n', [P2])); format('~s~n', [P1])
 	)).
 
 game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
@@ -73,7 +73,7 @@ game_loop_2players(P1, P2, Play, [BL,BB,BI]) :-
 		game_loop_2players(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
+		(W = -1, format('~s~n', [P2])); format('~s~n', [P1])
 	)).
 
 game_loop_player_bot(P1,P2,Play,[BL,BB,BI]) :-
@@ -90,7 +90,7 @@ game_loop_player_bot(P1,P2,Play,[BL,BB,BI]) :-
 		game_loop_player_bot(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
+		(W = -1, format('~s~n', [P2])); format('~s~n', [P1])
 	)).
 
 
@@ -107,7 +107,7 @@ game_loop_player_bot(P1,P2,Play,[BL,BB,BI]) :-
 		game_loop_player_bot(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
+		(W = -1, format('~s~n', [P2])); format('~s~n', [P1])
 	)).
 
 
@@ -125,7 +125,7 @@ game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
 		game_loop_2bots(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
+		(W = -1, format('~s~n', [P2])); format('~s~n', [P1])
 	)).
 
 game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
@@ -141,7 +141,7 @@ game_loop_2bots(P1,P2,Play,[BL,BB,BI]) :-
 		game_loop_2bots(P1,P2,NextPlay,R)
 	);(
 		write('Winner is '), 
-		(W = -1, write(P2)); write(P1)
[…]

### 2019-12-26 gap/main.pl
Added gap puzzle

@@ -1,0 +1,67 @@
+/**	PLOG 2019/2020
+ *	Joao Campos e Leonardo Moura
+ *	Gap puzzle
+ *	Two shaded squares in every row and column
+ *	Shaded squares do not touch, even at corners.
+ *	Numbers on the side indicate number of squares between shaded squares in that row or column.
+ *
+ *	Main file
+ */
+
+:-use_module(library(clpfd)).
+
+%	gap(+Side, -Out)
+%	generate solutions for the gap puzzle
+%	solutions come in the form of coordinates for black cells
+gap(S, Points) :-
+	number(S),								% check S is number
+
+	% get list of coordinates
+	N is 4 * S,
+	Max is S - 1,
+	length(Points, N),
+
+	%restrict the coordinates
+	domain(Points, 0, Max),
+	restrict(Points),
+
+	% find solution
+	labeling([], Points),
+	print_coords(Points).
+
+%	restrict(+Points)
+%	restrict all points
+restrict(Points) :-
+	restrict_first_line(Points, Rest, Prev),
+	restrict_all_lines(Rest, Prev).
+
+%	restrict_first_line(+Points, -Rest, -Line)
+%	restrict first line and return the Rest of the list and the first Line
+restrict_first_line([X1,Y1,X2,Y2|R], R, [X1,Y1,X2,Y2]) :-
+	Y1 #= Y2,
+	X2 #> X1 + 1.
+
+%	restrict_all_lines(+Points, +Prev)
+%	restrict all lines in board based on Previous line
+restrict_all_lines([], _) :- true.
+restrict_all_lines([X3,Y3,X4,Y4|R], [X1,Y1,X2,_]) :-
+	Y3 #= Y4,
+	X4 #> X3 + 1,
+
+	Y3 #= Y1 + 1,
+
+	X3 #\= X1,
+	X3 #\= X1 + 1,
+	X3 #\= X1 - 1,
+
+	X4 #\= X2,
+	X4 #\= X2 + 1,
+	X4 #\= X2 - 1,
+	restrict_all_lines(R, [X3,Y3,X4,Y4]).
+
+%	print(+Points)
+%	print puzzle using coordinates
+print_coords([]) :- true.
+print_coords([X1,Y1,X2,Y2|R]) :-
+	write('('), write(X1), write(' , '), write(Y1), write(')    ('), write(X2), write(' , '), write(Y2), write(')'),
+	nl, print_coords(R).

### 2019-12-26 gap/article/llncs2e/article.tex
Added latex article template with probably final title

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Solving Gap\thanks{Supported by no one lol}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{João Pedro Pinheiro de Lacerda Campos\inst{1} \and
Leonardo Fernandes Moura\inst{1}}
%
\authorrunning{J. Campos L. Moura}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculdade de Engenharia da Universidade do Porto,
Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL
\email{feup@fe.up.pt}\\
\url{http://www.fe.up.pt}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2020-01-04 gap/main.pl
Added board display

@@ -9,6 +9,7 @@
  */
 
 :-use_module(library(clpfd)).
+:-include('display.pl').
 
 %	gap(+Side, -Out)
 %	generate solutions for the gap puzzle

### 2020-01-04 gap/main.pl
.

@@ -8,6 +8,7 @@
  *	Main file
  */
 
+:-use_module(library(lists)).
 :-use_module(library(clpfd)).
 
 %	gap(+Side, -Out)
@@ -23,6 +24,7 @@ gap(S, Points) :-
 
 	%restrict the coordinates
 	domain(Points, 0, Max),
+	write('0 to '),write(Max),nl,
 	restrict(Points),
 
 	% find solution
@@ -32,36 +34,69 @@ gap(S, Points) :-
 %	restrict(+Points)
 %	restrict all points
 restrict(Points) :-
-	restrict_first_line(Points, Rest, Prev),
-	restrict_all_lines(Rest, Prev).
+	write('Start restrict'),nl,write(Points),nl,
+	restrict(Points, 0, [], [], []).
 
-%	restrict_first_line(+Points, -Rest, -Line)
-%	restrict first line and return the Rest of the list and the first Line
-restrict_first_line([X1,Y1,X2,Y2|R], R, [X1,Y1,X2,Y2]) :-
-	Y1 #= Y2,
-	X2 #> X1 + 1.
+%	restrict(+Points, N, prevX, occX, occY)
+%	restrict all points. 
+% N is number of line, 
+% prevX is list of invalid X (cells will touch), 
+% occX is list of occupied X, occY is list of occupied Y
+restrict([X1,Y1,X2,Y2,X3,Y3,X4,Y4 | R], N, prevX, occX, occY) :-
+	% if N was already used -> jump to next
+	count_duplicate(occY,N,I)												,
+	I = 0																						,
+	% restrict X
+	all_distinct([X1,X3|prevX])											,
+	X3 #> X1 + 1																		,
+	% restrict P1 and P2
+	X1 #= X2																				, 
+	Y1 #= N 																				, 
+	Y2 #> Y1 + 1																		,
+	% restrict P3 and P4
+	X3 #= X4																				, 
+	Y3 #= N 																				, 
+	Y4 #> Y3 + 1																		,
+	% prepare next iteration
+	append([Y1,Y2,Y3,Y4],occY,newOccY)							,
+	append([X1,X3],occX,newOccX)										,
+	BX1 #= X1 - 1																		, 
+	AX1 #= X1 + 1																		, 
+	BX3 #= X3 - 1																		, 
+	AX3 #= X3 + 1																		, 
[…]

### 2020-01-04 gap/article/llncs2e/article.tex
Added article skeleton

@@
 %
-\title{Solving Gap\thanks{Supported by no one lol}}
+\title{Gap}
+
+\subtitle{Puzzle solving using Prolog constraints}
 %
@@
 %
-\author{João Pedro Pinheiro de Lacerda Campos\inst{1} \and
-Leonardo Fernandes Moura\inst{1}}
+\author{João Pedro Pinheiro de Lacerda Campos\inst{1,2} \and
+Leonardo Fernandes Moura\inst{1,2}}
 %
@@
 %
-\institute{Faculdade de Engenharia da Universidade do Porto,
+
+\institute{
+Faculdade de Engenharia da Universidade do Porto,
 Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL
 \email{feup@fe.up.pt}\\
-\url{http://www.fe.up.pt}}
+\url{http://www.fe.up.pt} \and
+Logical Programing Course, Class 3MIEIC03, Group Gap Puzzle\_5}
+
 %
@@
 \end{abstract}
-%
-%
-%
-\section{First Section}
+
+\section{Introduction}
+
+\section{Problem Description}
+
+\section{Approach}
+
+\subsection{Decision Variables}
+
+\subsection{Constraints}
+
+\subsection{Evaluation Function}
+
+\section{Search Strategy}
+
+\section{Solution Presentation}
+
+\section{Results}
+
+\section{Conclusions and Future Work}
+
+\begin{thebibliography}{8}
+    \bibitem{ref_article1}
+    Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
+
+    \bibitem{ref_lncs1}
+    Author, F., Author, S.: Title of a proceedings paper. In: Editor,
+    F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
+    Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+
+    \bibitem{ref_book1}
+    Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
+    Location (1999)
+
+    \bibitem{ref_proc1}
+    Author, A.-B.: Contribution title. In: 9th International Proceedings
+    on Proceedings, pp. 1--2. Publisher, Location (2010)
+
+    \bibitem{ref_url1}
+    LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
+    Oct 2017
+    \end{thebibliography}
+
+% Article sampkes  REMOVE IN THE END
+\section{Introduction}
 \subsection{A Subsection Sample}

### 2020-01-04 gap/main.pl
fix autism

@@ -25,30 +25,28 @@ gap(S, Points) :-
 
 	%restrict the coordinates
 	domain(Points, 0, Max),
-	write('0 to '),write(Max),nl,
 	restrict(Points),
 
 	% find solution
-	labeling([], Points),
-	print_coords(Points).
+	labeling([], Points).
 
 %	restrict(+Points)
 %	restrict all points
 restrict(Points) :-
-	write('Start restrict'),nl,write(Points),nl,
+	write('Start restrict'),nl,
 	restrict(Points, 0, [], [], []).
 
-%	restrict(+Points, N, prevX, occX, occY)
+%	restrict(+Points, N, PrevX, OccX, OccY)
 %	restrict all points. 
 % N is number of line, 
-% prevX is list of invalid X (cells will touch), 
-% occX is list of occupied X, occY is list of occupied Y
-restrict([X1,Y1,X2,Y2,X3,Y3,X4,Y4 | R], N, prevX, occX, occY) :-
+% PrevX is list of invalid X (cells will touch), 
+% OccX is list of occupied X, OccY is list of occupied Y
+restrict([X1,Y1,X2,Y2,X3,Y3,X4,Y4 | R], N, PrevX, OccX, OccY) :-
 	% if N was already used -> jump to next
-	count_duplicate(occY,N,I)												,
+	count_duplicate(OccY,N,I)												,
 	I = 0																						,
 	% restrict X
-	all_distinct([X1,X3|prevX])											,
+	all_distinct([X1,X3|PrevX])											,
 	X3 #> X1 + 1																		,
 	% restrict P1 and P2
 	X1 #= X2																				, 
@@ -59,41 +57,39 @@ restrict([X1,Y1,X2,Y2,X3,Y3,X4,Y4 | R], N, prevX, occX, occY) :-
 	Y3 #= N 																				, 
 	Y4 #> Y3 + 1																		,
 	% prepare next iteration
-	append([Y1,Y2,Y3,Y4],occY,newOccY)							,
-	append([X1,X3],occX,newOccX)										,
+	append([Y1,Y2,Y3,Y4],OccY,NewOccY)							,
+	append([X1,X3],OccX,NewOccX)										,
 	BX1 #= X1 - 1																		, 
 	AX1 #= X1 + 1																		, 
 	BX3 #= X3 - 1																		, 
 	AX3 #= X3 + 1																		, 
 	NN is N + 1																			,
[…]

### 2020-01-04 gap/article/llncs2e/article.tex
Added article first part

@@
 %
-\title{Gap}
+\title{Gap Puzzles}
 
@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+This project was developed during the the Logical Programing Course in the context of the year
+of the Integrated Masters in in Informatics and Computing Engineering at The Faculty of Engineering
+of the University of Porto. The goal was to solve a problem using the Prolog programming language,
+more specifically, using Constraint Logic Programming over Finite Domains (clpfd) library, that's defined
+in the SICStus Prolog distribution. 
+In the specific case of our team, the problem in question is the Gap Puzzle, which is defined in detail in
+\textbf{Section 2}.
+In order to solve the problem, Prolog constraint programming was used. This type of programming grants us the
+advantage of fast computation, requiring a somewhat simple and little verbosed kind of programming. Using constraints,
+we can simply define all the constraints of our problem (in the case of puzzles these are the rules of the puzzle), 
+which in the case of more complex problems is not trivial. Then, after defining the solution search algorithm, 
+the clpfd library will search for solutions.
+\textbf{CONCLUSÕES}
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Prolog  \and Constraint Programing \and Gap Puzzle.}
 \end{abstract}
 
+\pagebreak
+
 \section{Introduction}
+\paragraph{}
+This goal of the project was to elaborate a Prolog program that, given a board order, computes all the solutions of the 
+Gap Puzzle for that board order. 
+Optimization is a relevant factor here. Different ways of defining constraints can lead us to the same set of 
+solutions, but computation times can vary greatly. So, one of the concerns during the development of this project 
+was to find solutions as fast as possible.
+
+\paragraph{}
+Bellow we shortly explain the following sections of this article.
+
+\begin{itemize}
+    \item \textbf{Problem Description:} Detailed description of the problem we are solving and the rules of Gap Puzzles
+
+    \item \textbf{Approach:} 
+    \begin{itemize}
+        \item \textbf{Decision Variables:} 
+        \item \textbf{Constraints:}
+        \item \textbf{Search Strategy:} 
+    \end{itemize}
+
+    \item \textbf{Solution Presentation:} Description of how solutions are presented in an intelligible way.
+    \item \textbf{Results:}
+    \item \textbf{Conclusions:}
+\end{itemize}
 
 \section{Problem Description}
+The problem in question is the solution is the solution of the Gap Puzzle. Gap is a very simple puzzle, yet a challenging
+one. We have grid of arbitrary size and our goal, is to shade two squares of the grid in every row and column, such that 
+two shaded squares do not touch, even at the corners. Because there is more than one solution for every grid order,
+in the puzzle form of the problem, there are numbers on the side of the grid to indicate the number of non shaded squares
+there must exist between two shaded squares in that row or column. The figure below illustrates an example of puzzle with
+order 5.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{images/figure1.png}
+\caption{Gap Puzzle example} \label{fig1}
+\end{figure}
+
+\paragraph{}
+Although they are very interesting, these specific puzzles do not interest us. We are interested in finding arbitrary 
+solutions for a problem with a given order.
 
@@
 
-\subsection{Evaluation Function}
-
 \section{Search Strategy}
@@
 \section{Solution Presentation}
+\paragraph{}
+For solution presentation there the \textbf{display\_gap(+Sol,+Len)} was elaborated. This predicate receives the \textit{Sol}
+list, which is a prolog list containing the coordinates of all grid cells to be shaded for that solution, and \textit{Len},
+which is the length of a row, that is, the order of the board the solution given applies to. In order to do this, this 
+predicate uses the three predicates explained bellow.
+
+\paragraph{}
+This predicate uses the \textbf{empty\_board(-B,+Len)} which creates a list of lists representing an empty grid, with order \textit{Len},
+this new grid is then unified with \textit{B}. This predicate works by appending new atoms, representing an empty cell (\textbf{' '}, 
+a single space character) to an empty starting list. Once this list has the desired length, this list is then replicated 
+several times to form a new empty grid.
+
+\paragraph{}
+Then, we use the \textbf{process\_board(+Board,+Sol,-NewBoard)} to substitute all the empty cells in the positions given
+by solution list, with the \textbf{'X'} atom. This represents a shaded cell. In order to make the substitution we defined
+the \textbf{replaceN(+List,+N,+NewElem,Res)} predicate. This predicate substitutes the element of order \textit{N} in 
+\textit{List} to the element \textit{NewElem}, then unifies the resulting list with \textit{NewBoard}.
+
+\paragraph{}
+Finally, the predicate \textbf{display\_board(+Board)} was defined to display the board \textit{Board}. This predicate
+writes the separators in the screen and then displays each row of the grid, using the right format. Bellow, we can see a
+displayed board.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/fig2.png}
+        \caption{Solution Display Example} \label{fig2}
+    \end{center}
+\end{figure}
 
@@
 \begin{thebibliography}{8}
-    \bibitem{ref_article1}
-    Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-    \bibitem{ref_lncs1}
-    Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-    F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-    Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-    \bibitem{ref_book1}
-    Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-    Location (1999)
-
-    \bibitem{ref_proc1}
-    Author, A.-B.: Contribution title. In: 9th International Proceedings
-    on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-    \bibitem{ref_url1}
-    LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-    Oct 2017
+    \bibitem{ref_url}
+    Erich Friedman's Puzzle Palace - Gap Puzzles, Copyright Erich Friedman, 2010. 
+    \url{https://www2.stetson.edu/~efriedma/puzzle/gap/}. 
+    Last accessed 4 Jan 2020
     \end{thebibliography}

### 2020-01-04 gap/main.pl
this

@@ -19,77 +19,42 @@ gap(S, Points) :-
 	number(S),								% check S is number
 
 	% get list of coordinates
-	N is 4 * S,
 	Max is S - 1,
-	length(Points, N),
+	length(Left, S),
+	length(Right, S),
+	length(Up, S),
+	length(Down, S),
 
-	%restrict the coordinates
-	domain(Points, 0, Max),
-	restrict(Points),
+	domain(Left, 0, Max),
+	domain(Right, 0, Max),
+	domain(Up, 0, Max),
+	domain(Down, 0, Max),
+
+	all_distinct(Left),
+	all_distinct(Right),
+	all_distinct(Up),
+	all_distinct(Down),
+
+	restrict(Left, Right, Up, Down, Points),
+	nl,nl,write(Points),nl,nl,
 
 	% find solution
-	labeling([], Points).
+	labeling([], Points),
+	display_gap(Points,S).
 
 %	restrict(+Points)
 %	restrict all points
-restrict(Points) :-
-	write('Start restrict'),nl,
-	restrict(Points, 0, [], [], []).
-
-%	restrict(+Points, N, PrevX, OccX, OccY)
-%	restrict all points. 
-% N is number of line, 
-% PrevX is list of invalid X (cells will touch), 
-% OccX is list of occupied X, OccY is list of occupied Y
-restrict([X1,Y1,X2,Y2,X3,Y3,X4,Y4 | R], N, PrevX, OccX, OccY) :-
-	% if N was already used -> jump to next
-	count_duplicate(OccY,N,I)												,
-	I = 0																						,
-	% restrict X
-	all_distinct([X1,X3|PrevX])											,
-	X3 #> X1 + 1																		,
-	% restrict P1 and P2
-	X1 #= X2																				, 
-	Y1 #= N 																				, 
-	Y2 #> Y1 + 1																		,
-	% restrict P3 and P4
-	X3 #= X4																				, 
-	Y3 #= N 																				, 
-	Y4 #> Y3 + 1																		,
-	% prepare next iteration
-	append([Y1,Y2,Y3,Y4],OccY,NewOccY)							,
-	append([X1,X3],OccX,NewOccX)										,
-	BX1 #= X1 - 1																		, 
-	AX1 #= X1 + 1																		, 
-	BX3 #= X3 - 1																		, 
[…]

### 2020-01-05 gap/main.pl
IT IS DONW

@@ -12,49 +12,133 @@
 :-use_module(library(clpfd)).
 :-include('display.pl').
 
+restrict_two(Sol,0) :- count(0,Sol,#=,2).
+
+restrict_two(Sol,S) :-
+	count(S,Sol,#=,2),
+	Next is S-1,
+	restrict_two(Sol,Next).
+
+restrict_next_pair([],_,_).
+
+restrict_next_pair([HX,HY|T],X,Y) :-
+	#\((HX #= X + 1) #/\ (HY #= Y + 1)),
+	#\((HX #= X + 1) #/\ (HY #= Y - 1)),
+	#\((HX #= X - 1) #/\ (HY #= Y + 1)),
+	#\((HX #= X - 1) #/\ (HY #= Y - 1)),
+	#\((HX #= X + 1) #/\ (HY #= Y)),
+	#\((HX #= X - 1) #/\ (HY #= Y)),
+	#\((HX #= X) #/\ (HY #= Y - 1)),
+	#\((HX #= X) #/\ (HY #= Y + 1)),
+	#\((HX #= X) #/\ (HY #= Y)),
+	restrict_next_pair(T,X,Y).
+
+restrict_next_(_,[]).
+
+restrict_next_(Prev,[X,Y|T]) :-
+	append(Prev,T,L),
+	restrict_next_pair(L,X,Y),
+	append(Prev,[X,Y],Next),
+	restrict_next_(Next,T).
+
+restrict_next(List) :-
+	restrict_next_([],List).
+
+extractX_([],Res,Res).
+
+extractX_([X,_|T],Acc,Res) :-
+	extractX_(T,[X|Acc],Res).
+
+extractX(List,Pairs) :-
+	extractX_(List,[],Pairs).
+
+extractY_([],Res,Res).
+
+extractY_([_,Y|T],Acc,Res) :-
+	extractY_(T,[Y|Acc],Res).
+
+extractY(List,Pairs) :-
+	extractY_(List,[],Pairs).
+
+crescent_order([_,_]).
+
+crescent_order([X1,Y1,X2,Y2|T]) :-
+	X1 #>= X2, 
+	#\((X1 #= X2) #<=> (Y1 #> Y2)),
+	crescent_order([X2,Y2|T]).
+
+crescent_order([H1,H2|T]) :-
+	H1 #>= H2, 
+	crescent_order([H2|T]).
+
+
+gap_(S,Points) :-
+	Max is 4 * S,
+	Dom is S -1,
+
[…]

### 2020-01-05 gap/main.pl
Removed underscore lol

@@ -72,7 +72,7 @@ crescent_order([H1,H2|T]) :-
 	crescent_order([H2|T]).
 
 
-gap_(S,Points) :-
+gap(S,Points) :-
 	Max is 4 * S,
 	Dom is S -1,
 

### 2020-01-05 gap/article/llncs2e/article.tex
Added part 3 of the report, now sleep

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/figure1.png}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/figure1.png}
         \caption{Gap Puzzle example} \label{fig1}
+    \end{center}
 \end{figure}
@@
 
+\pagebreak
+
 \section{Approach}
+\paragraph{}
+In the specific context of this problem, the constraints used to solve the problem are a translation of the rules of 
+the puzzle to Prolog Constraints. The following subsections explain the constraints used in detail.
 
 \subsection{Decision Variables}
+To solve this problem we have only a decision variable, the \textit{Points} list. This list stores the coordinates of all
+the cells that will be shaded, in the format \textit{[X1,Y1,X2,Y2|...]}. We start by defining that this list will have a 
+a length of:
+
+\begin{equation}
+    points = 2 * order
+\end{equation}
+
+\begin{equation}
+    length = 4 * order
+\end{equation}
+
+This happens because we can only have two shaded cells in each row. Since the number of rows is equal to the order of our
+grid, we a number of points that is two times our order.
+
+\paragraph{}
+Then we define the domain of the Decision Variable, this will between zero and the number immediately inferior to our order,
+this is because we are considering a system of coordinates starting in zero.
 
 \subsection{Constraints}
+\paragraph{}
+The first constraint we make is to grant there are only two shaded cells in each row and in each column. We do this 
+using the \textbf{restrict\_two(+List,+Order)} predicate. This predicate restricts each number of the domain in the list 
+to occur exactly two times in the list. We do this two times, the first for a list containing all the X coordinates of the
+solution, and a second time for the Y coordinate. We are able to split this using the \textbf{extractX(+List,-XList)} and
+\textbf{extractY(+List,-YList)} predicates. The first one takes a list with the solution format and unifies in 
+\textit{XList} all the X coordinates of that list. The \textit{extractY} predicate does the same for Y.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/restrict_two.png}
+        \caption{The restrict\_two predicate} \label{fig2}
+    \end{center}
+\end{figure}
+
+\paragraph{}
+Then we restrict the positions of the shaded cells themselves. We do this using the \textbf{restrict\_next(+List)} predicate.
+This predicate iterates through the list making sure that no other coordinates in the list are the coordinates of an 
+adjacent cell to the any of the other cells and that no two cell coordinates are the same. This predicate calls the
+\textbf{restrict\_next\_pair(+List,+X,+Y)} predicate that applies the constraints mentioned above to all the other 
+coordinate pairs in the list.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/restrictPair.png}
+        \caption{The restrict\_next\_pair predicate} \label{fig3}
+    \end{center}
+\end{figure}
 
 \section{Search Strategy}
+\paragraph{}
+So that prolog can search for arbitrary solutions and not different permutations of the same solution, we need to define
+a predicate that makes each solution unique. In the present case, this was accomplished by ordering all the points 
+of a solution in a crescent order, making each solution unique. This is accomplished by the \textbf{crescent\_order(+List)}
+predicate.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/crescent.png}
+        \caption{The crescent\_order predicate} \label{fig4}
+    \end{center}
+\end{figure}
 

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 %
-% If you use the hyperref package, please uncomment the following line
+% If you use the hyperref package, please uncomment the following line1
 % to display URLs in blue roman font according to Springer's eBook style:
@@
 This project was developed during the the Logical Programing Course in the context of the year
-of the Integrated Masters in in Informatics and Computing Engineering at The Faculty of Engineering
+of the Integrated Masters in Informatics and Computing Engineering at The Faculty of Engineering
 of the University of Porto. The goal was to solve a problem using the Prolog programming language,
@@
 the clpfd library will search for solutions.
-\textbf{CONCLUSÕES}
 
@@
 
-    \item \textbf{Approach:} 
+    \item \textbf{Approach}
     \begin{itemize}
-        \item \textbf{Decision Variables:} 
-        \item \textbf{Constraints:}
-        \item \textbf{Search Strategy:} 
+        \item \textbf{Decision Variables}
+        \item \textbf{Constraints}
+        \item \textbf{Search Strategy}
     \end{itemize}
@@
 \section{Problem Description}
-The problem in question is the solution is the solution of the Gap Puzzle. Gap is a very simple puzzle, yet a challenging
+The problem in question is the solution of the Gap Puzzle. Gap is a very simple puzzle, yet a challenging
 one. We have grid of arbitrary size and our goal, is to shade two squares of the grid in every row and column, such that
@@
 there must exist between two shaded squares in that row or column. The figure below illustrates an example of puzzle with
-order 5.
+order 9.
 
@@
 \end{equation}
-
 \begin{equation}
@@
 \paragraph{}
-Then we define the domain of the Decision Variable, this will between zero and the number immediately inferior to our order,
+Then we define the domain of the decision variable, which is between zero and the number immediately inferior to our order,
 this is because we are considering a system of coordinates starting in zero.
@@
 \paragraph{}
-The first constraint we make is to grant there are only two shaded cells in each row and in each column. We do this 
+The first constraint we make is to ensure there are only two shaded cells in each row and in each column. We do this
 using the \textbf{restrict\_two(+List,+Order)} predicate. This predicate restricts each number of the domain in the list
@@
 \paragraph{}
-So that prolog can search for arbitrary solutions and not different permutations of the same solution, we need to define
+To ensure that prolog only searches for different solutions and not different permutations of the same solution, we need to define
 a predicate that makes each solution unique. In the present case, this was accomplished by ordering all the points
@@
 \paragraph{}
-For solution presentation there the \textbf{display\_gap(+Sol,+Len)} was elaborated. This predicate receives the \textit{Sol}
-list, which is a prolog list containing the coordinates of all grid cells to be shaded for that solution, and \textit{Len},
-which is the length of a row, that is, the order of the board the solution given applies to. In order to do this, this 
-predicate uses the three predicates explained bellow.
+For solution presentation we elaborated \textbf{display\_gap(+Sol,+Len)}. This predicate receives the \textit{Points}
+list, with the format previously explained, and \textit{Order}, which is the order of the board the solution given applies to.
+This predicate then uses the three predicates explained bellow.
 
 \paragraph{}
-This predicate uses the \textbf{empty\_board(-B,+Len)} which creates a list of lists representing an empty grid, with order \textit{Len},
-this new grid is then unified with \textit{B}. This predicate works by appending new atoms, representing an empty cell (\textbf{' '}, 
+Firstly it uses \textbf{empty\_board(-B,+Len)} predicate which creates a list of lists representing an empty grid, with order \textit{Len},
+this new grid is then unified with \textit{B}.
+This predicate works by appending new atoms, representing an empty cell (\textbf{\textquotesingle \textquotesingle},
 a single space character) to an empty starting list. Once this list has the desired length, this list is then replicated
@@
 Then, we use the \textbf{process\_board(+Board,+Sol,-NewBoard)} to substitute all the empty cells in the positions given
-by solution list, with the \textbf{'X'} atom. This represents a shaded cell. In order to make the substitution we defined
-the \textbf{replaceN(+List,+N,+NewElem,Res)} predicate. This predicate substitutes the element of order \textit{N} in 
-\textit{List} to the element \textit{NewElem}, then unifies the resulting list with \textit{NewBoard}.
+by solution list, with the \textbf{\textquotesingle X \textquotesingle} atom.
+This represents a shaded cell. In order to make the substitution we defined
+the \textbf{replaceN(+List,+N,+NewElem,-Res)} predicate. This predicate substitutes the element of order \textit{N} in
+\textit{List} to the element \textit{NewElem}, then unifies the resulting list with \textit{Res}.
 
@@
 \section{Results}
+Our program finds one solution for every order given. Given this, we tested it with all possible numbers from 1 to 30.
+By doing this we discovered that the puzzle only has solutions with orders 9 and above. Here are two examples.
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/gap9.jpg}
+        \caption{Solution Example} \label{fig3}
+    \end{center}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/gap11.jpg}
+        \caption{Solution Example} \label{fig4}
+    \end{center}
+\end{figure}
+After making multiple tries per order we ended up with this graph. It shows the amount of time taken by the program for
+each order.
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/graph.png}
+        \caption{Times Graph} \label{fig5}
+    \end{center}
+\end{figure}
+From the graph you can see a pattern where the program takes exponentially more time to solve the puzzle. But then it
+reaches a point where there is a drop in that time. This pattern repeats itself after its first instance and probably forever, as you increase order.
 
 \section{Conclusions and Future Work}
+We think we have achieved what was proposed to us at the start of this project. With this work we were able to learn how to think in a different way.
+Since we use other paradigms of programming more frequently, when using prolog with restrictions we could not think of a solution to the problem as quickly as normal.
+As previously said, the gap puzzle is a challenging one, but with the use of restrictions, we can find solutions in little time.
+\paragraph{}
+From the results we can conclude that our proposed solution is not perfect. How is it possible for such a big time difference from one solution to another?
+And why are there bigger boards with considerably smaller times then smaller boards?
+\paragraph{}
+We could say one advantage to our solution is the fact that it finds one and only one solution per board size. This means it loses less time evaluating several solutions.
+Although this feature can also be seen as a limitation, since we can only get one solution and miss the other ones.
 

### 2020-01-05 gap/main.pl

@@ -10,6 +10,7 @@
 
 :-use_module(library(lists)).
 :-use_module(library(clpfd)).
+:-use_module(library(statistics)).
 :-include('display.pl').
 
 restrict_two(Sol,0) :- count(0,Sol,#=,2).
@@ -73,6 +74,7 @@ crescent_order([H1,H2|T]) :-
 
 
 gap(S,Points) :-
+  statistics(walltime, [Start,_]),
 	Max is 4 * S,
 	Dom is S -1,
 
@@ -88,12 +90,12 @@ gap(S,Points) :-
 	restrict_two(YList,Dom),
 
 	restrict_next(Points),
-
-	write(labeling), nl,
-
 	labeling([],Points),
-	display_gap(Points,S).
-	
+  statistics(walltime, [End,_]),
+	display_gap(Points,S),
+        
+  Time is End - Start,
+	format('finished ~3d seconds.~n', [Time]).
 
  
 %	gap(+Side, -Out)

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 By doing this we discovered that the puzzle only has solutions with orders 9 and above. Here are two examples.
+
 \begin{figure}
@@
 \end{figure}
+
+\paragraph{}
 After making multiple tries per order we ended up with this graph. It shows the amount of time taken by the program for
-each order.
+each order. From the graph you can see a pattern where the program takes exponentially more time to solve the puzzle. But then it
+reaches a point where there is a drop in that time. This pattern repeats itself after its first instance and probably forever, as you increase order.
+
 \begin{figure}
     \begin{center}
-        \includegraphics[scale=0.5]{images/graph.png}
+        \includegraphics[scale=0.6]{images/graph.png}
         \caption{Times Graph} \label{fig5}
@@
 \end{figure}
-From the graph you can see a pattern where the program takes exponentially more time to solve the puzzle. But then it
-reaches a point where there is a drop in that time. This pattern repeats itself after its first instance and probably forever, as you increase order.
 
@@
 
-% Article sampkes  REMOVE IN THE END
-\section{Introduction}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 \end{document}

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 \section{Results}
+\paragraph{}
 Our program finds one solution for every order given. Given this, we tested it with all possible numbers from 1 to 30.
@@
 \section{Conclusions and Future Work}
+\paragraph{}
 We think we have achieved what was proposed to us at the start of this project. With this work we were able to learn how to think in a different way.

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 
-\section{Search Strategy}
+\subsection{Search Strategy}
 \paragraph{}
-To ensure that prolog only searches for different solutions and not different permutations of the same solution, we need to define
-a predicate that makes each solution unique. In the present case, this was accomplished by ordering all the points
-of a solution in a crescent order, making each solution unique. This is accomplished by the \textbf{crescent\_order(+List)}
-predicate.
+Initially, we opted to use an ordering function to order the coordinates. This way, we would only get one solution and not
+permutations of the same solution. Later, while doing timed tests, we noticed irregularities. To combat these, we found
+a new way to search solutions, a random function. After adding this function to our project and removing the precious
+ordering one, we noticed great improvement in our tests.
 
@@
     \begin{center}
-        \includegraphics[scale=0.5]{images/crescent.png}
-        \caption{The crescent\_order predicate} \label{fig4}
+        \includegraphics[scale=0.4]{images/random.png}
+        \caption{Random selection predicate} \label{fig4}
     \end{center}
@@
 this new grid is then unified with \textit{B}.
-This predicate works by appending new atoms, representing an empty cell (\textbf{\textquotesingle \textquotesingle},
+This predicate works by appending new atoms, representing an empty cell (\textbf{' '},
 a single space character) to an empty starting list. Once this list has the desired length, this list is then replicated
@@
 Then, we use the \textbf{process\_board(+Board,+Sol,-NewBoard)} to substitute all the empty cells in the positions given
-by solution list, with the \textbf{\textquotesingle X \textquotesingle} atom.
+by solution list, with the \textbf{' X '} atom.
 This represents a shaded cell. In order to make the substitution we defined
@@
     \begin{center}
-        \includegraphics[scale=0.5]{images/gap9.jpg}
+        \includegraphics[scale=0.35]{images/gap9.jpg}
         \caption{Solution Example} \label{fig3}
@@
         \includegraphics[scale=0.6]{images/graph.png}
-        \caption{Times Graph} \label{fig5}
+        \caption{Times graph} \label{fig5}
+    \end{center}
+\end{figure}
+
+\paragraph{}
+This irregular behaviour told us the solution was imperfect somewhere. With that knowledge, we felt incentivized to search new ways of labeling variables.
+We then found we could add a random function to the labeling and once we implemented it, it showed incredible results.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.6]{images/graph2.png}
+        \caption{Times graph after random labeling} \label{fig5}
     \end{center}
@@
 Since we use other paradigms of programming more frequently, when using prolog with restrictions we could not think of a solution to the problem as quickly as normal.
+\paragraph{}
 As previously said, the gap puzzle is a challenging one, but with the use of restrictions, we can find solutions in little time.
+One significant thing we learned was that a change that might seem simple, as adding a random function, might increase efficiency by many times.
 \paragraph{}
-From the results we can conclude that our proposed solution is not perfect. How is it possible for such a big time difference from one solution to another?
-And why are there bigger boards with considerably smaller times then smaller boards?
-\paragraph{}
-We could say one advantage to our solution is the fact that it finds one and only one solution per board size. This means it loses less time evaluating several solutions.
-Although this feature can also be seen as a limitation, since we can only get one solution and miss the other ones.
+From the results we can conclude that our program is quite efficient and that is one of its advantages. But this is at the cost of certainty, since you only get random
+solutions, maybe not the one you are looking for.
 

### 2020-01-05 gap/main.pl

@@ -11,6 +11,7 @@
 :-use_module(library(lists)).
 :-use_module(library(clpfd)).
 :-use_module(library(statistics)).
+:-use_module(library(random)).
 :-include('display.pl').
 
 restrict_two(Sol,0) :- count(0,Sol,#=,2).
@@ -64,12 +65,12 @@ extractY(List,Pairs) :-
 crescent_order([_,_]).
 
 crescent_order([X1,Y1,X2,Y2|T]) :-
-	X1 #>= X2, 
+	X1 #>= X2,
 	#\((X1 #= X2) #<=> (Y1 #> Y2)),
 	crescent_order([X2,Y2|T]).
 
 crescent_order([H1,H2|T]) :-
-	H1 #>= H2, 
+	H1 #>= H2,
 	crescent_order([H2|T]).
 
 
@@ -84,71 +85,21 @@ gap(S,Points) :-
 	extractX(Points,XList),
 	extractY(Points,YList),
 
-	crescent_order(Points),
+	%crescent_order(Points),
 
 	restrict_two(XList,Dom),
 	restrict_two(YList,Dom),
 
 	restrict_next(Points),
-	labeling([],Points),
+	labeling([value(selRandom)],Points),
   statistics(walltime, [End,_]),
 	display_gap(Points,S),
-        
+
   Time is End - Start,
 	format('finished ~3d seconds.~n', [Time]).
 
- 
-%	gap(+Side, -Out)
-%	generate solutions for the gap puzzle
-%	solutions come in the form of coordinates for black cells
-% gap(S, Points) :-
-% 	number(S),								% check S is number
-
-% 	% get list of coordinates
-% 	Max is S - 1,
-% 	length(Left, S),
-% 	length(Right, S),
-% 	length(Up, S),
-% 	length(Down, S),
-
-% 	domain(Left, 0, Max),
-% 	domain(Right, 0, Max),
-% 	domain(Up, 0, Max),
-% 	domain(Down, 0, Max),
-
-% 	all_distinct(Left),
-% 	all_distinct(Right),
-% 	all_distinct(Up),
-% 	all_distinct(Down),
-
-% 	restrict(Left, Right, Up, Down, Points),
-% 	nl,nl,write(Points),nl,nl,
-
-% 	% find solution
-% 	labeling([], Points),
-% 	display_gap(Points,S).
-
-% %	restrict(+Points)
-% %	restrict all points
[…]

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 \paragraph{}
-Initially, we opted to use an ordering function to order the coordinates. This way, we would only get one solution and not
-permutations of the same solution. Later, while doing timed tests, we noticed irregularities. To combat these, we found
-a new way to search solutions, a random function. After adding this function to our project and removing the precious
-ordering one, we noticed great improvement in our tests.
+For labeling we made an ordering function in \textbf{crescent\_order(+B)} predicate. This predicate orders the coordinates of the points
+top-down and left-right, improving the labeling times for smaller boards.
 
@@
     \begin{center}
-        \includegraphics[scale=0.4]{images/random.png}
+        \includegraphics[scale=0.5]{images/crescent.png}
+        \caption{Crescent ordering} \label{fig4}
+    \end{center}
+\end{figure}
+
+\paragraph{}
+For bigger boards, \textbf{crescent\_order(+B)} predicate is an expensive task, as it runs through the whole list of points to apply the restrictions.
+For this reason, if the board is of order 15 or bigger, this predicate is not used.
+\paragraph{}
+We also added a random function that was given in the classes. This function allows \textbf{labeling} predicate to select the value in a random way.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.5]{images/random.png}
         \caption{Random selection predicate} \label{fig4}
@@
 This irregular behaviour told us the solution was imperfect somewhere. With that knowledge, we felt incentivized to search new ways of labeling variables.
-We then found we could add a random function to the labeling and once we implemented it, it showed incredible results.
+We then found we could add a random function to the labeling and once we implemented it, it showed incredible results. After more testing, we reached the conclusion
+that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+B)}, but to bigger boards it was a waste of time. With this in mind,
+we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+B)}.
 
@@
     \begin{center}
-        \includegraphics[scale=0.6]{images/graph2.png}
+        \includegraphics[scale=0.5]{images/graph2.png}
         \caption{Times graph after random labeling} \label{fig5}

### 2020-01-05 gap/main.pl

@@ -85,7 +85,7 @@ gap(S,Points) :-
 	extractX(Points,XList),
 	extractY(Points,YList),
 
-	%crescent_order(Points),
+	((S < 15, crescent_order(Points));true),
 
 	restrict_two(XList,Dom),
 	restrict_two(YList,Dom),

### 2020-01-05 gap/article/llncs2e/article.tex
report

@@
 \paragraph{}
-For labeling we made an ordering function in \textbf{crescent\_order(+B)} predicate. This predicate orders the coordinates of the points
-top-down and left-right, improving the labeling times for smaller boards.
+For labeling we made an ordering function in \textbf{crescent\_order(+List)} predicate. This predicate orders the coordinates of the points
+down-top and right-left, improving the labeling times for smaller boards.
 
@@
         \includegraphics[scale=0.5]{images/crescent.png}
-        \caption{Crescent ordering} \label{fig4}
+        \caption{Point ordering} \label{fig4}
     \end{center}
@@
 \paragraph{}
-For bigger boards, \textbf{crescent\_order(+B)} predicate is an expensive task, as it runs through the whole list of points to apply the restrictions.
+For bigger boards, \textbf{crescent\_order(+List)} predicate is an expensive task, as it runs through the whole list of points to apply the restrictions.
 For this reason, if the board is of order 15 or bigger, this predicate is not used.
@@
 
+\newpage
+
 \section{Results}
@@
 Our program finds one solution for every order given. Given this, we tested it with all possible numbers from 1 to 30.
-By doing this we discovered that the puzzle only has solutions with orders 9 and above. Here are two examples.
+By doing this we discovered that the puzzle only has solutions with orders 9 and above. Here is one example of one board with order 11.
 
@@
     \end{center}
-    \begin{center}
-        \includegraphics[scale=0.5]{images/gap11.jpg}
-        \caption{Solution Example} \label{fig4}
-    \end{center}
 \end{figure}
 
+\pagebreak
+
 \paragraph{}
-After making multiple tries per order we ended up with this graph. It shows the amount of time taken by the program for
+After making multiple tries per order we ended up with this graph. It shows the amount of time (in seconds) taken by the program for
 each order. From the graph you can see a pattern where the program takes exponentially more time to solve the puzzle. But then it
@@
     \begin{center}
-        \includegraphics[scale=0.6]{images/graph.png}
+        \includegraphics[scale=0.5]{images/graph.png}
         \caption{Times graph} \label{fig5}
@@
 We then found we could add a random function to the labeling and once we implemented it, it showed incredible results. After more testing, we reached the conclusion
-that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+B)}, but to bigger boards it was a waste of time. With this in mind,
-we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+B)}.
+that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+List)}, but to bigger boards it was a waste of time. With this in mind,
+we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+List)}, but bigger boards it would not.
 
@@
 
+\pagebreak
 \section{Conclusions and Future Work}

### 2020-01-05 gap/main.pl

@@ -75,28 +75,41 @@ crescent_order([H1,H2|T]) :-
 
 
 gap(S,Points) :-
+	S < 15,
   statistics(walltime, [Start,_]),
 	Max is 4 * S,
 	Dom is S -1,
-
 	length(Points,Max),
 	domain(Points,0,Dom),
-
 	extractX(Points,XList),
 	extractY(Points,YList),
-
-	((S < 15, crescent_order(Points));true),
-
+	crescent_order(Points),
 	restrict_two(XList,Dom),
 	restrict_two(YList,Dom),
-
 	restrict_next(Points),
 	labeling([value(selRandom)],Points),
   statistics(walltime, [End,_]),
 	display_gap(Points,S),
-
   Time is End - Start,
-	format('finished ~3d seconds.~n', [Time]).
+	format('finished in ~3d seconds.~n', [Time]).
+
+gap(S,Points) :-
+	S >= 15,
+  statistics(walltime, [Start,_]),
+	Max is 4 * S,
+	Dom is S -1,
+	length(Points,Max),
+	domain(Points,0,Dom),
+	extractX(Points,XList),
+	extractY(Points,YList),
+	restrict_two(XList,Dom),
+	restrict_two(YList,Dom),
+	restrict_next(Points),
+	labeling([value(selRandom)],Points),
+  statistics(walltime, [End,_]),
+	display_gap(Points,S),
+  Time is End - Start,
+	format('finished in ~3d seconds.~n', [Time]).
 
 selRandom(Var, Rest, BB0, BB1):- % seleciona valor de forma aleatória
    fd_set(Var, Set), fdset_to_list(Set, List),

### 2020-01-05 gap/article/llncs2e/article.tex
formatting code

@@
 \paragraph{}
-Our program finds one solution for every order given. Given this, we tested it with all possible numbers from 1 to 30.
-By doing this we discovered that the puzzle only has solutions with orders 9 and above. Here is one example of one board with order 11.
+Our program finds a solution given a valid number above 0. Given this, we tested it with all possible numbers from 1 to 30.
+By doing this we discovered that the puzzle only has solutions for orders 9 and above. Here is one example of one board with order 11.
 
@@
     \begin{center}
-        \includegraphics[scale=0.5]{images/graph.png}
-        \caption{Times graph} \label{fig5}
+        \includegraphics[scale=0.38]{images/graph.png}
+        \caption{Times graph order/time(s)} \label{fig5}
     \end{center}
@@
 This irregular behaviour told us the solution was imperfect somewhere. With that knowledge, we felt incentivized to search new ways of labeling variables.
-We then found we could add a random function to the labeling and once we implemented it, it showed incredible results. After more testing, we reached the conclusion
-that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+List)}, but to bigger boards it was a waste of time. With this in mind,
-we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+List)}, but bigger boards it would not.
+Before we only ordered the values of the coordinates before labeling.
+We then found we could add a random function to the labeling and once we implemented it, it showed incredible results.
 
@@
         \includegraphics[scale=0.5]{images/graph2.png}
-        \caption{Times graph after random labeling} \label{fig5}
+        \caption{Times graph after random labeling order/time(s)} \label{fig5}
+    \end{center}
+\end{figure}
+After more testing, we reached the conclusion
+that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+List)}, but to bigger boards it wasted too much time. With this in mind,
+we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+List)}, but bigger boards it would not.
+\begin{figure}
+    \begin{center}
+        \includegraphics[scale=0.3]{images/graph3.png}
+        \caption{Times graph after random labeling and condition for bigger boards \newline order/time(s)} \label{fig5}
     \end{center}
@@
 \paragraph{}
-From the results we can conclude that our program is quite efficient and that is one of its advantages. But this is at the cost of certainty, since you only get random
-solutions, maybe not the one you are looking for.
+From the results we can conclude that our program is quite efficient and that is one of its advantages.
 
@@
 
+\appendix
+\section{\\Annex}
+\paragraph{}
+Within the zip this article came in, are present the source code files for the project and images and data used for this article.
+
 \end{document}

### 2020-01-05 gap/auxiliar.pl

@@ -1,0 +1,64 @@
+restrict_two(Sol,0) :- count(0,Sol,#=,2).
+
+restrict_two(Sol,S) :-
+	count(S,Sol,#=,2),
+	Next is S-1,
+	restrict_two(Sol,Next).
+
+restrict_next_pair([],_,_).
+
+restrict_next_pair([HX,HY|T],X,Y) :-
+	#\((HX #= X + 1) #/\ (HY #= Y + 1)),
+	#\((HX #= X + 1) #/\ (HY #= Y - 1)),
+	#\((HX #= X - 1) #/\ (HY #= Y + 1)),
+	#\((HX #= X - 1) #/\ (HY #= Y - 1)),
+	#\((HX #= X + 1) #/\ (HY #= Y)),
+	#\((HX #= X - 1) #/\ (HY #= Y)),
+	#\((HX #= X) #/\ (HY #= Y - 1)),
+	#\((HX #= X) #/\ (HY #= Y + 1)),
+	#\((HX #= X) #/\ (HY #= Y)),
+	restrict_next_pair(T,X,Y).
+
+restrict_next_(_,[]).
+
+restrict_next_(Prev,[X,Y|T]) :-
+	append(Prev,T,L),
+	restrict_next_pair(L,X,Y),
+	append(Prev,[X,Y],Next),
+	restrict_next_(Next,T).
+
+restrict_next(List) :-
+	restrict_next_([],List).
+
+extractX_([],Res,Res).
+
+extractX_([X,_|T],Acc,Res) :-
+	extractX_(T,[X|Acc],Res).
+
+extractX(List,Pairs) :-
+	extractX_(List,[],Pairs).
+
+extractY_([],Res,Res).
+
+extractY_([_,Y|T],Acc,Res) :-
+	extractY_(T,[Y|Acc],Res).
+
+extractY(List,Pairs) :-
+	extractY_(List,[],Pairs).
+
+crescent_order([_,_]).
+
+crescent_order([X1,Y1,X2,Y2|T]) :-
+	X1 #>= X2,
+	#\((X1 #= X2) #<=> (Y1 #> Y2)),
+	crescent_order([X2,Y2|T]).
+
+crescent_order([H1,H2|T]) :-
+	H1 #>= H2,
+	crescent_order([H2|T]).
+
+selRandom(Var, Rest, BB0, BB1):- % seleciona valor de forma aleatória
+   fd_set(Var, Set), fdset_to_list(Set, List),
[…]

### 2020-01-05 gap/auxiliar.pl
formating code

@@ -1,12 +1,21 @@
-restrict_two(Sol,0) :- count(0,Sol,#=,2).
+/**	PLOG 2019/2020
+ *	Joao Campos e Leonardo Moura
+ *	Gap puzzle
+ *	Two shaded squares in every row and column
+ *	Shaded squares do not touch, even at corners.
+ *
+ *	Auxiliar file
+ */
 
+% restrict_two/2
+% restrict number of duplicates of each number to 2
+restrict_two(Sol,0) :- count(0,Sol,#=,2).
 restrict_two(Sol,S) :-
 	count(S,Sol,#=,2),
 	Next is S-1,
 	restrict_two(Sol,Next).
 
 restrict_next_pair([],_,_).
-
 restrict_next_pair([HX,HY|T],X,Y) :-
 	#\((HX #= X + 1) #/\ (HY #= Y + 1)),
 	#\((HX #= X + 1) #/\ (HY #= Y - 1)),
@@ -20,43 +29,45 @@ restrict_next_pair([HX,HY|T],X,Y) :-
 	restrict_next_pair(T,X,Y).
 
 restrict_next_(_,[]).
-
 restrict_next_(Prev,[X,Y|T]) :-
 	append(Prev,T,L),
 	restrict_next_pair(L,X,Y),
 	append(Prev,[X,Y],Next),
 	restrict_next_(Next,T).
 
+% restrict_next/1
+% restrict coordinates so 2 points do not touch
 restrict_next(List) :-
 	restrict_next_([],List).
 
 extractX_([],Res,Res).
+extractX_([X,_|T],Acc,Res) :- extractX_(T,[X|Acc],Res).
 
-extractX_([X,_|T],Acc,Res) :-
-	extractX_(T,[X|Acc],Res).
-
-extractX(List,Pairs) :-
-	extractX_(List,[],Pairs).
+% extractX/2
+% extract every second element starting from first
+extractX(List,Pairs) :- extractX_(List,[],Pairs).
 
 extractY_([],Res,Res).
+extractY_([_,Y|T],Acc,Res) :- extractY_(T,[Y|Acc],Res).
 
-extractY_([_,Y|T],Acc,Res) :-
-	extractY_(T,[Y|Acc],Res).
-
+% extractY/2
+% extract every second element
 extractY(List,Pairs) :-
 	extractY_(List,[],Pairs).
 
+% crescent_order/1
+% order coordinates in list
 crescent_order([_,_]).
-
[…]

### 2020-01-05 gap/main.pl

@@ -3,7 +3,6 @@
  *	Gap puzzle
  *	Two shaded squares in every row and column
  *	Shaded squares do not touch, even at corners.
- *	Numbers on the side indicate number of squares between shaded squares in that row or column.
  *
  *	Main file
  */
@@ -13,82 +12,30 @@
 :-use_module(library(statistics)).
 :-use_module(library(random)).
 :-include('display.pl').
-
-restrict_two(Sol,0) :- count(0,Sol,#=,2).
-
-restrict_two(Sol,S) :-
-	count(S,Sol,#=,2),
-	Next is S-1,
-	restrict_two(Sol,Next).
-
-restrict_next_pair([],_,_).
-
-restrict_next_pair([HX,HY|T],X,Y) :-
-	#\((HX #= X + 1) #/\ (HY #= Y + 1)),
-	#\((HX #= X + 1) #/\ (HY #= Y - 1)),
-	#\((HX #= X - 1) #/\ (HY #= Y + 1)),
-	#\((HX #= X - 1) #/\ (HY #= Y - 1)),
-	#\((HX #= X + 1) #/\ (HY #= Y)),
-	#\((HX #= X - 1) #/\ (HY #= Y)),
-	#\((HX #= X) #/\ (HY #= Y - 1)),
-	#\((HX #= X) #/\ (HY #= Y + 1)),
-	#\((HX #= X) #/\ (HY #= Y)),
-	restrict_next_pair(T,X,Y).
-
-restrict_next_(_,[]).
-
-restrict_next_(Prev,[X,Y|T]) :-
-	append(Prev,T,L),
-	restrict_next_pair(L,X,Y),
-	append(Prev,[X,Y],Next),
-	restrict_next_(Next,T).
-
-restrict_next(List) :-
-	restrict_next_([],List).
-
-extractX_([],Res,Res).
-
-extractX_([X,_|T],Acc,Res) :-
-	extractX_(T,[X|Acc],Res).
-
-extractX(List,Pairs) :-
-	extractX_(List,[],Pairs).
-
-extractY_([],Res,Res).
-
-extractY_([_,Y|T],Acc,Res) :-
-	extractY_(T,[Y|Acc],Res).
-
-extractY(List,Pairs) :-
-	extractY_(List,[],Pairs).
-
-crescent_order([_,_]).
-
-crescent_order([X1,Y1,X2,Y2|T]) :-
-	X1 #>= X2,
[…]

### 2020-01-05 gap/display.pl
.

@@ -1,85 +1,84 @@
 :- use_module(library(lists)).
 
 generate_line_(L,L,0) :- !.
-
 generate_line_(L,Aux,Len) :-
     Next is Len - 1,
     generate_line_(L,[' '|Aux],Next).
 
+% generate_line/2
+% generate line of ' ' with length Len
 generate_line(L,Len) :-
     generate_line_(L,[],Len).
 
 
 empty_board_(B,_,B,0) :- !.
-
 empty_board_(B,Line,Aux,Len) :-
     Next is Len -1,
     empty_board_(B,Line,[Line|Aux],Next).
 
+% empty_board/2
+% create empty board of order Len
 empty_board(B,Len) :-
     generate_line(L,Len),
     empty_board_(B,L,[],Len).
 
 
 replaceN_([],_,_,Aux,Res) :- reverse(Aux, Res).
-
 replaceN_([_|T],0,NewElem,Aux,Res) :-
     replaceN_(T,-1,NewElem,[NewElem|Aux],Res), !.
-
 replaceN_([H|T],N,NewElem,Aux,Res) :-
     Next is N - 1,
     replaceN_(T,Next,NewElem,[H|Aux],Res).
 
+% replaceN/4
+% replace Nth element with NewElem
 replaceN(List,N,NewElem,Res) :-
     length(List, Len),
     N =< Len,
     replaceN_(List,N,NewElem,[],Res).
 
-
+% process_board/3
+% turn coordinate list of points into board for display
 process_board(NewBoard,[],NewBoard).
-
 process_board(B,[X,Y|Tail],NewBoard) :-
     nth0(Y,B,Line),
     replaceN(Line,X,'X',NewLine),
     replaceN(B,Y,NewLine,TempNewBoard),
     process_board(TempNewBoard,Tail,NewBoard).
 
+% write_separator/1
+% write line separator for board display
 write_separator(0) :- write('+'),!, nl.
-
 write_separator(Len) :-
     write('+---'),
     Next is Len - 1,
     write_separator(Next).
 
 % display_board(+Board)
+% display Board on the screen
 display_board(B) :- 
     length(B, Len),
 	display_board(B,Len), !.
-
 display_board([L|T],Len) :- 
 	Len >= 0,
 	write_separator(Len),
 	draw_line(L), nl,
 	display_board(T,Len).
-
 display_board([],Len) :- write_separator(Len).
 
 % display_line(+Line)
+% display single line
[…]

### 2020-01-05 gap/main.pl

@@ -14,9 +14,12 @@
 :-include('display.pl').
 :-include('auxiliar.pl').
 
+% gap/2
+% gap(+S, -Points).
+% find a solution to gap puzzle with order S
 gap(S,Points) :-
 	S < 15,
-  statistics(walltime, [Start,_]),
+  	statistics(walltime, [Start,_]),
 	Max is 4 * S,
 	Dom is S -1,
 
@@ -37,12 +40,12 @@ gap(S,Points) :-
 	statistics(walltime, [End,_]),
 
 	display_gap(Points,S),
-  Time is End - Start,
+  	Time is End - Start,
 	format('finished in ~3d seconds.~n', [Time]).
 
 gap(S,Points) :-
 	S >= 15,
-  statistics(walltime, [Start,_]),
+  	statistics(walltime, [Start,_]),
 	Max is 4 * S,
 	Dom is S -1,
 
@@ -61,5 +64,5 @@ gap(S,Points) :-
 	statistics(walltime, [End,_]),
 
 	display_gap(Points,S),
-  Time is End - Start,
+  	Time is End - Start,
 	format('finished in ~3d seconds.~n', [Time]).
